### 2018-04-02 paper.tex
Added paper and code

\documentclass[]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
% \usepackage{txfonts}

\begin{document}
\title{Distinguishing NFW and Isothermal Density Profiles with Gravitational Lensing}
\author{}
\date{\today}
\maketitle

\begin{abstract}
    abstract!!
\end{abstract}

\section{Introduction}

\subsection{General spherical density profile $\rho(r)$}
Using thin lens approximation

Projected surface density at radius R
\begin{equation}
    \Sigma(R) = \int_{-\infty}^{\infty}{\rho(\sqrt{R^2 + z^2}) dz}
\end{equation}

Average projected surface density within radius R
\begin{equation}
    \overline{\Sigma}(R) = \frac{1}{\pi R^2} \int_0^{2\pi}{d\phi \int_0^{R}{dR'~\Sigma(R')R'}}
\end{equation}

Critical surface density
\begin{equation}
    \Sigma_\mathrm{crit} = \frac{c^2}{4\pi G} \frac{D_S}{D_{SL} D_L}
\end{equation}

Convergence at radius R
\begin{equation}
    \kappa(R) = \frac{\Sigma(R)}{\Sigma_\mathrm{crit}}
\end{equation}

Tangential shear at radius R
\begin{equation}
    \gamma(R) = \overline{\kappa}(R) - \kappa(R)
\end{equation}

Deflection angle
\begin{equation}
    \vec{\alpha}(\vec{\theta}) = \overline{\kappa}(\theta)\vec{\theta}
\end{equation}

Ellipticity

prove that spherical density profiles only have tangential shear

\newpage

\subsection{Navarro-Frenk-White (NFW) Profile}

\begin{equation}
    \rho_\mathrm{NFW}(r) = \frac{\rho_\mathrm{crit} \delta_c}{(r/r_s)\left(1 + r/r_s\right)^2}
\end{equation}

\begin{equation}
    \Sigma_\mathrm{NFW}(R) = \frac{2 \rho_\mathrm{crit} \delta_c r_s}{(R/r_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(R/r_s)^2 - 1}} \right) \arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right)
\end{equation}
[Bartelmann 2001]

\begin{equation}
    \overline{\Sigma}_\mathrm{NFW}(R) = \frac{4 \rho_\mathrm{crit} \delta_c r_s}{(R/r_s)^2} \left(
        \frac{2}{\sqrt{(R/r_s)^2 - 1}} ~\arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) + \ln{\left(\frac{R/r_s}{2}\right)}
    \right)
\end{equation}

\begin{equation}
    \gamma(R) =
\end{equation}

We switch the dependence to $M_{200}$ and $c$ with:

\begin{equation}
    \delta_c = \frac{200}{3} \frac{c^3}{\ln(1 + c) - c/(1 + c)}
\end{equation}

\begin{equation}
    r_s = \frac{1}{c} \left(\frac{3M_{200}}{800\pi \rho_\mathrm{crit}}\right)^\frac{1}{3}
\end{equation}

\subsection{Cored Isothermal Sphere Profile}

\begin{equation}
    \rho_\mathrm{iso}(r) = \frac{\sigma^2}{2\pi G (r^2 + {r_c}^2)}
\end{equation}

\begin{equation}
    \Sigma_\mathrm{iso}(R) = \frac{\sigma^2}{2 G \sqrt{R^2 + {r_c}^2}}
\end{equation}

\begin{equation}
    \overline{\Sigma}_\mathrm{iso}(R) = \frac{\sigma^2 \left(\sqrt{R^2 + {r_c}^2} - r_c \right)}{G R^2}
\end{equation}

\begin{equation}
    \gamma(R) = \frac{\sigma^2 \left(\sqrt{R^2 + {r_c}^2} - r_c \right)}{\Sigma_\mathrm{crit} G R^2} - \frac{\sigma^2}{2 \Sigma_\mathrm{crit} G \sqrt{R^2 + {r_c}^2}}
\end{equation}

\subsection{Current plan}
\begin{itemize}
    \item Calculate tangential shear and deflection angle for NFW and SIS
    \item Consider single foreground lens halo with many
    \item How to arrange and distribute background halos?
    \begin{itemize}
        \item Initial ellipticity
        \item angular density on sky
        \item sizes
    \end{itemize}
    \item Apply shear and deflection angle to background galaxies
    \item Attempt to fit both profiles, subtracting intrinsic shear, see if the fit is distinguishable
    \item How many foreground halos to test?

\end{itemize}

\section{Methods}

\end{document}

### 2018-04-02 stuff.py

@@ -1,0 +1,28 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+class NFWHalo:
+
+    def __init__(self, M200, c):
+        self.M200 = M200
+        self.c = c
+
+    def averageConvergence(R):
+        pass
+
+    def shear():
+        pass
+
+class IsothermalHalo:
+
+    def __init__(self, sigma, rc):
+        self.sigma = sigma
+        self.rc = rc
+
+    def averageConvergence():
+        pass
+
+class BackgroundGalaxy:
+
+    def __init__(self, DS, DSL):
+        self.arg = arg

### 2018-04-02 stuff.py
Added link for ellipses

@@ -26,3 +26,5 @@ class BackgroundGalaxy:
 
     def __init__(self, DS, DSL):
         self.arg = arg
+
+# https://matplotlib.org/examples/pylab_examples/ellipse_demo.html

### 2018-04-03 stuff.py
Now creates basic lensed images

@@ -1,30 +1,78 @@
 import numpy as np
 import matplotlib.pyplot as plt
+from matplotlib.patches import Ellipse
+
+c = 1
+G = 1
+RHO_CRIT = 1
+
+def SIGMA_CRIT(DS, DL):
+    DSL = DS - DL
+    return c**2 / (4 * np.pi * G) * (DS / (DSL * DL))
+
 
 class NFWHalo:
 
-    def __init__(self, M200, c):
+    def __init__(self, M200, c, DL):
         self.M200 = M200
         self.c = c
+        self.delta_c = (200/3) * c**3 / (np.log(1+c) - c/(1+c))
+        self.rs = 1/c * ((3 * M200) / (800 * np.pi * RHO_CRIT))**(1/3)
+        self.DL = DL
 
-    def averageConvergence(R):
-        pass
-
-    def shear():
-        pass
 
 class IsothermalHalo:
 
-    def __init__(self, sigma, rc):
+    def __init__(self, sigma, rc, DL):
         self.sigma = sigma
         self.rc = rc
+        self.DL = DL
 
-    def averageConvergence():
-        pass
+    def surfaceDensity(self, R):
+        return self.sigma**2 / (2 * G * np.sqrt(R**2 + self.rc**2))
+
+    def averageSurfaceDensity(self, R):
+        return self.sigma**2 * (np.sqrt(R**2 + self.rc**2) - self.rc) / (G * R**2)
+
+    def shear(self, R, DS):
+        return (self.averageSurfaceDensity(R) - self.surfaceDensity(R)) / SIGMA_CRIT(DS, self.DL)
+
+    def ellipticity(self, R, DS):
+        reducedShear = self.shear(R, DS) / (1 - self.averageSurfaceDensity(R) / SIGMA_CRIT(DS, self.DL))
+        return 2 * reducedShear / (1 + reducedShear**2)
+
+    def lense(self, galaxy):
+        R = np.sqrt(galaxy.x**2 + galaxy.y**2)
+        phi = np.degrees(np.arctan2(galaxy.y, galaxy.x))
+        epsilon = self.ellipticity(R, galaxy.DS)
+        area_scaling = np.sqrt(1 / (1 - epsilon))
+        return Ellipse(xy=[galaxy.x, galaxy.y], width=(1-epsilon)*galaxy.size, height=galaxy.size, angle=phi)
+
 
 class BackgroundGalaxy:
 
-    def __init__(self, DS, DSL):
[…]

### 2018-04-03 lensing.py
Renamed files

@@ -62,7 +62,7 @@ class BackgroundGalaxy:
 
 
 halo = IsothermalHalo(1, 1, 1)
-backgroundGalaxies = [BackgroundGalaxy(1, 3, 100*np.random.rand()-50, 100*np.random.rand()-50, 300) for i in range(300)]
+backgroundGalaxies = [BackgroundGalaxy(1, 3, 100*np.random.rand()-50, 100*np.random.rand()-50, 10) for i in range(300)]
 
 fig = plt.figure(dpi=150)
 ax = fig.add_subplot(111, aspect='equal')

### 2018-04-03 lensing.py
collaborative coding !

@@ -1,10 +1,18 @@
 import numpy as np
 import matplotlib.pyplot as plt
 from matplotlib.patches import Ellipse
+import astropy.cosmology as cosmology
+from astropy.visualization import astropy_mpl_style
+import astropy.units as u
+import astropy.constants as const
 
-c = 1
-G = 1
-RHO_CRIT = 1
+plt.style.use(astropy_mpl_style)
+
+c = const.c
+G = const.G
+H0 = cosmology.default_cosmology.get().H(0)
+RHO_CRIT = 3 * H0**2 / (8 * np.pi * G)
+
 
 def SIGMA_CRIT(DS, DL):
     DSL = DS - DL
@@ -42,37 +50,67 @@ class IsothermalHalo:
         return 2 * reducedShear / (1 + reducedShear**2)
 
     def lense(self, galaxy):
-        R = np.sqrt(galaxy.x**2 + galaxy.y**2)
-        phi = np.degrees(np.arctan2(galaxy.y, galaxy.x))
-        epsilon = self.ellipticity(R, galaxy.DS)
+        beta = np.sqrt(galaxy.beta_x**2 + galaxy.beta_y**2)
+        phi = np.degrees(np.arctan2(galaxy.beta_y, galaxy.beta_x))
+        epsilon = self.ellipticity(self.DL*beta.to_value(u.rad), galaxy.DS)
         area_scaling = np.sqrt(1 / (1 - epsilon))
-        return Ellipse(xy=[galaxy.x, galaxy.y], width=(1-epsilon)*galaxy.size, height=galaxy.size, angle=phi)
+        # deflection angle: beta -> theta
+        return LensedBackgroundGalaxy(galaxy.beta_x, galaxy.beta_y, galaxy.a, galaxy.e1, galaxy.e2, galaxy.DS)
 
 
 class BackgroundGalaxy:
 
-    def __init__(self, e_intrinsic, size, x, y, DS):
+    def __init__(self, beta_x, beta_y, a, e1, e2, DS):
+        self.beta_x = beta_x
+        self.beta_y = beta_y
+        self.a = a
+        self.e1 = e1
+        self.e2 = e2
         self.DS = DS
-        self.e_intrinsic = e_intrinsic
-        self.size = size
-        self.x = x
-        self.y = y
-        self.ellipse = Ellipse(xy=[x,y], width=size, height=size, angle=0)
+
[…]

### 2018-04-10 paper.tex
Added link for ellipses
Now creates basic lensed images
Renamed files
Notes from meeting

@@
 \begin{abstract}
-    abstract!!
+
 \end{abstract}
@@
 Ellipticity
+\begin{equation}
+    \epsilon(R) = \frac{2 \gamma/(1 - \kappa)}{1 + (\gamma/(1 - \kappa))^2}
+\end{equation}
 
-prove that spherical density profiles only have tangential shear
+Prove that spherical density profiles only have tangential shear and ellipticity
 
@@
     \item Calculate tangential shear and deflection angle for NFW and SIS
-    \item Consider single foreground lens halo with many
+    \item Consider single foreground lens halo with many background galaxies
     \item How to arrange and distribute background halos?
@@
     \item How many foreground halos to test?
+    \item What redshift is $\rho_\mathrm{crit}$ evaluated at?
 
 \end{itemize}
+
+N sets of e1, e2, theta1, theta2
+
+Analyzing data:
+make histogram in annulus
+mean and standard deviation
+use log bins for theta
+
+50 gals/square arcminute
+5 arcminutes
+z_L = 0.3
+z_S = 1
+M_halo = 10^15 solar masses
+instrinsic ellipticity from gaussian with width 0.2
 

### 2018-04-10 lensing.py

@@ -49,6 +49,9 @@ class IsothermalHalo:
         reducedShear = self.shear(R, DS) / (1 - self.averageSurfaceDensity(R) / SIGMA_CRIT(DS, self.DL))
         return 2 * reducedShear / (1 + reducedShear**2)
 
+    def deflection(beta, ):
+        dd
+
     def lense(self, galaxy):
         beta = np.sqrt(galaxy.beta_x**2 + galaxy.beta_y**2)
         phi = np.degrees(np.arctan2(galaxy.beta_y, galaxy.beta_x))
@@ -87,8 +90,8 @@ class LensedBackgroundGalaxy:
         self.DS = DS
 
     def ellipse(self):
-        a = 1
-        b = 1
+        a = .01
+        b = .01
         phi = 1
         x = (self.DS * self.theta_x.to_value(u.rad)).to_value(u.Mpc)
         y = (self.DS * self.theta_y.to_value(u.rad)).to_value(u.Mpc)
@@ -105,7 +108,7 @@ backgroundGalaxies = [BackgroundGalaxy(
     DS=10*u.Gpc) for i in range(300)]
 
 fig = plt.figure(dpi=150)
-ax = fig.add_subplot(111, aspect='equal')
+ax = fig.add_subplot(111, aspect="equal")
 
 for gal in backgroundGalaxies:
     lensedGal = halo.lense(gal)

### 2018-04-10 datagenerator.py
created datagenerator.py

@@ -1,0 +1,15 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.patches import Ellipse
+import astropy.cosmology as cosmology
+from astropy.visualization import astropy_mpl_style
+import astropy.units as u
+import astropy.constants as const
+
+from lensing import NFWHalo
+from lensing import IsothermalHalo
+
+# data format is theta_x, theta_y, e1, e2
+datafile = open('output.txt','w')
+datafile.write("Hello world")
+datafile.close()

### 2018-04-10 datagenerator.py
added comments. functionally identical

@@ -1,3 +1,13 @@
+"""
+Created by Doyee Byun
+April 10, 2018
+
+Goals:
+Figure out how to create data using code from lensing.py
+define initial conditions for creating data
+galaxy locations, lens profile, etc.
+"""
+
 import numpy as np
 import matplotlib.pyplot as plt
 from matplotlib.patches import Ellipse
@@ -6,10 +16,11 @@ from astropy.visualization import astropy_mpl_style
 import astropy.units as u
 import astropy.constants as const
 
+#import profiles from lensing.py
 from lensing import NFWHalo
 from lensing import IsothermalHalo
 
 # data format is theta_x, theta_y, e1, e2
 datafile = open('output.txt','w')
-datafile.write("Hello world")
+datafile.write("Hello world") #Dummy code for testing write function
 datafile.close()

### 2018-04-10 datagenerator.py
dummy code changed to fit format

@@ -22,5 +22,5 @@ from lensing import IsothermalHalo
 
 # data format is theta_x, theta_y, e1, e2
 datafile = open('output.txt','w')
-datafile.write("Hello world") #Dummy code for testing write function
+datafile.write("0.5\t0.5\t1\t1") #Dummy code for testing write function
 datafile.close()

### 2018-04-17 datagenerator.py
newlines need newline characters

@@ -22,5 +22,7 @@ from lensing import IsothermalHalo
 
 # data format is theta_x, theta_y, e1, e2
 datafile = open('output.txt','w')
-datafile.write("0.5\t0.5\t1\t1") #Dummy code for testing write function
+datafile.write("0.5\t0.5\t1\t1\n") #Dummy code for testing write function
+datafile.write("Newline?\n")
+datafile.writelines(["haha\n","hoho\n"])
 datafile.close()

### 2018-04-17 paper.tex
Updates to article

@@
 \begin{equation}
-    \gamma(R) = \overline{\kappa}(R) - \kappa(R)
+    \gamma_t(R) = \overline{\kappa}(R) - \kappa(R)
 \end{equation}
+
+\[\gamma_1 = -\gamma_t \cos{2\phi}\]
+\[\gamma_2 = -\gamma_t \sin{2\phi}\]
 
@@
 
+We switch dependence from $\sigma^2$ to $M_{200}$ with:
+
+\begin{equation}
+    r_{200} = \left( \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}} \right)^{1/3}
+\end{equation}
+
+\begin{equation}
+    \sigma^2 = \frac{G M_{200}}{2 \left(
+        \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}}
+        - r_c \arctan \left(
+            \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit} {r_c}^3}
+        \right)
+    \right)}
+\end{equation}
+
+$M_{200}$ is defined as:
+\begin{equation}
+    M_{200} = M_{enc}(r_{200}) = 200 \rho_\mathrm{crit} \frac{4}{3} \pi r_{200}^3
+\end{equation}
+
 \subsection{Current plan}
@@
     \item Attempt to fit both profiles, subtracting intrinsic shear, see if the fit is distinguishable
-    \item How many foreground halos to test?
-    \item What redshift is $\rho_\mathrm{crit}$ evaluated at?
+    \item How many foreground halos to test? - start with 1
+    \item What redshift is $\rho_\mathrm{crit}$ evaluated at? - at halo redshift
 
@@
 5 arcminutes
-z_L = 0.3
-z_S = 1
-M_halo = 10^15 solar masses
+$z_L = 0.3$
+$z_S = 1$
+$M_halo = 10^15$ solar masses
 instrinsic ellipticity from gaussian with width 0.2

### 2018-04-17 lensing.py

@@ -8,6 +8,7 @@ import astropy.constants as const
 
 plt.style.use(astropy_mpl_style)
 
+#Define constants
 c = const.c
 G = const.G
 H0 = cosmology.default_cosmology.get().H(0)
@@ -21,11 +22,11 @@ def SIGMA_CRIT(DS, DL):
 
 class NFWHalo:
 
-    def __init__(self, M200, c, DL):
+    def __init__(self, M200, c_param, DL):
         self.M200 = M200
-        self.c = c
-        self.delta_c = (200/3) * c**3 / (np.log(1+c) - c/(1+c))
-        self.rs = 1/c * ((3 * M200) / (800 * np.pi * RHO_CRIT))**(1/3)
+        self.c = c_param     #changed variable name for clarification
+        self.delta_c = (200/3) * c_param**3 / (np.log(1+c_param) - c_param/(1+c_param))
+        self.rs = 1/c_param * ((3 * M200) / (800 * np.pi * RHO_CRIT))**(1/3)
         self.DL = DL
 
 

### 2018-04-17 datagenerator.py
no effective changes. will uncomment and finish lines

@@ -21,7 +21,12 @@ from lensing import NFWHalo
 from lensing import IsothermalHalo
 
 # data format is theta_x, theta_y, e1, e2
-datafile = open('output.txt','w')
+#M200_0 =
+#c =
+#dl =
+
+datafile = open('output1','w')
+NFWHalo
 datafile.write("0.5\t0.5\t1\t1\n") #Dummy code for testing write function
 datafile.write("Newline?\n")
 datafile.writelines(["haha\n","hoho\n"])

### 2018-04-17 datagenerator.py
This should work, provided that we build a lense function for NFW later

@@ -19,15 +19,25 @@ import astropy.constants as const
 #import profiles from lensing.py
 from lensing import NFWHalo
 from lensing import IsothermalHalo
+from lensing import BackgroundGalaxy
 
 # data format is theta_x, theta_y, e1, e2
-#M200_0 =
-#c =
-#dl =
+M200_0 = 100*u.solMass
+c_param = 0.5
+dl = 1*u.Gpc
 
-datafile = open('output1','w')
-NFWHalo
-datafile.write("0.5\t0.5\t1\t1\n") #Dummy code for testing write function
-datafile.write("Newline?\n")
-datafile.writelines(["haha\n","hoho\n"])
+datafile = open('output1.txt','w')
+nfw_1 = NFWHalo(M200_0,c_param,dl)
+backgroundGalaxies = [BackgroundGalaxy(
+    beta_x=(100*np.random.rand()-50)*u.arcsec,
+    beta_y=(100*np.random.rand()-50)*u.arcsec,
+    e1=0,
+    e2=0,
+    a=1*u.arcsec,
+    DS=10*u.Gpc) for i in range(300)]
+for i in range(0,len(backgroundGalaxies)):
+    newGalx = nfw_1.lense(backgroundGalaxies[i])
+    datafile.write(newGalx.theta_x,"\t",newGalx.theta_y,"\t",newGalx.e1,"\t",newGalx.e2,"\t\n")
+#nfw_1.lens(galaxy_1)
+
 datafile.close()

### 2018-04-17 lensing.py

@@ -97,23 +97,23 @@ class LensedBackgroundGalaxy:
         y = (self.DS * self.theta_y.to_value(u.rad)).to_value(u.Mpc)
         return Ellipse(xy=[x,y], width=a, height=b, angle=phi)
 
+def main():
+    halo = IsothermalHalo(sigma=1*u.m/u.s, rc=1*u.Mpc, DL=1*u.Gpc)
+    backgroundGalaxies = [BackgroundGalaxy(
+        beta_x=(100*np.random.rand()-50)*u.arcsec,
+        beta_y=(100*np.random.rand()-50)*u.arcsec,
+        e1=0,
+        e2=0,
+        a=1*u.arcsec,
+        DS=10*u.Gpc) for i in range(300)]
 
-halo = IsothermalHalo(sigma=1*u.m/u.s, rc=1*u.Mpc, DL=1*u.Gpc)
-backgroundGalaxies = [BackgroundGalaxy(
-    beta_x=(100*np.random.rand()-50)*u.arcsec,
-    beta_y=(100*np.random.rand()-50)*u.arcsec,
-    e1=0,
-    e2=0,
-    a=1*u.arcsec,
-    DS=10*u.Gpc) for i in range(300)]
+    fig = plt.figure(dpi=150)
+    ax = fig.add_subplot(111, aspect="equal")
 
-fig = plt.figure(dpi=150)
-ax = fig.add_subplot(111, aspect="equal")
+    for gal in backgroundGalaxies:
+        lensedGal = halo.lense(gal)
+        lensedGalEllipse = lensedGal.ellipse()
+        lensedGalEllipse.set_facecolor(np.random.rand(3))
+        ax.add_artist(lensedGalEllipse)
 
-for gal in backgroundGalaxies:
-    lensedGal = halo.lense(gal)
-    lensedGalEllipse = lensedGal.ellipse()
-    lensedGalEllipse.set_facecolor(np.random.rand(3))
-    ax.add_artist(lensedGalEllipse)
-
-plt.show()
+    plt.show()

### 2018-04-17 datagenerator.py
comment added to clarify current state of code. (why no isothermal)

@@ -38,6 +38,8 @@ backgroundGalaxies = [BackgroundGalaxy(
 for i in range(0,len(backgroundGalaxies)):
     newGalx = nfw_1.lense(backgroundGalaxies[i])
     datafile.write(newGalx.theta_x,"\t",newGalx.theta_y,"\t",newGalx.e1,"\t",newGalx.e2,"\t\n")
-#nfw_1.lens(galaxy_1)
+
+#Isothermal Profile lensing will be added once the paramaters are modified
+#to be identical to those of NFW
 
 datafile.close()

### 2018-04-17 datagenerator.py
comments added

@@ -22,6 +22,8 @@ from lensing import IsothermalHalo
 from lensing import BackgroundGalaxy
 
 # data format is theta_x, theta_y, e1, e2
+
+#test parameters for lens
 M200_0 = 100*u.solMass
 c_param = 0.5
 dl = 1*u.Gpc

### 2018-04-17 paper.tex
paper - added things in terms of angles

@@
 \begin{abstract}
-
+We attempt to distinguish NFW and cored isothermal density profiles using weak gravitational lensing shear.
 \end{abstract}
@@
 Projected surface density at radius R
-\begin{equation}
-    \Sigma(R) = \int_{-\infty}^{\infty}{\rho(\sqrt{R^2 + z^2}) dz}
-\end{equation}
+\[\Sigma(R) = \int_{-\infty}^{\infty}{\rho(\sqrt{R^2 + z^2}) dz}\]
 
 Average projected surface density within radius R
-\begin{equation}
-    \overline{\Sigma}(R) = \frac{1}{\pi R^2} \int_0^{2\pi}{d\phi \int_0^{R}{dR'~\Sigma(R')R'}}
-\end{equation}
+\[\overline{\Sigma}(R) = \frac{1}{\pi R^2} \int_0^{2\pi}{d\phi \int_0^{R}{dR'~\Sigma(R')R'}}\]
 
 Critical surface density
-\begin{equation}
-    \Sigma_\mathrm{crit} = \frac{c^2}{4\pi G} \frac{D_S}{D_{SL} D_L}
-\end{equation}
+\[\Sigma_\mathrm{crit} = \frac{c^2}{4\pi G} \frac{D_S}{D_{SL} D_L}\]
 
-Convergence at radius R
-\begin{equation}
-    \kappa(R) = \frac{\Sigma(R)}{\Sigma_\mathrm{crit}}
-\end{equation}
+Convergence
+\[\kappa(\theta) = \frac{\Sigma(\theta)}{\Sigma_\mathrm{crit}}\]
 
-Tangential shear at radius R
-\begin{equation}
-    \gamma_t(R) = \overline{\kappa}(R) - \kappa(R)
-\end{equation}
-
+Tangential shear
+\[\gamma_t(\theta) = \overline{\kappa}(\theta) - \kappa(\theta)\]
 \[\gamma_1 = -\gamma_t \cos{2\phi}\]
 \[\gamma_2 = -\gamma_t \sin{2\phi}\]
+\[\gamma = \gamma_t = \sqrt{{\gamma_1}^2 + {\gamma_2}^2} = -\gamma_1 \cos{2\phi} -\gamma_2 \sin{2\phi}\]
 
 Deflection angle
-\begin{equation}
-    \vec{\alpha}(\vec{\theta}) = \overline{\kappa}(\theta)\vec{\theta}
-\end{equation}
+\[\vec{\alpha}(\vec{\theta}) = \overline{\kappa}(\theta)\vec{\theta}\]
+\[\vec{\beta} = \vec{\theta} - \vec{\alpha} = (1 - \overline{\kappa}(\theta))\vec{\theta} \]
 
 Ellipticity
-\begin{equation}
-    \epsilon(R) = \frac{2 \gamma/(1 - \kappa)}{1 + (\gamma/(1 - \kappa))^2}
-\end{equation}
+\[\epsilon_i = \frac{2 \gamma_i/(1 - \kappa)}{1 + \gamma^2/(1 - \kappa)^2}\]
+
+In small angle approximation, any length $R = D_L \theta$.
 
@@
 
-\newpage
-
-\subsection{Navarro-Frenk-White (NFW) Profile}
-
-\begin{equation}
-    \rho_\mathrm{NFW}(r) = \frac{\rho_\mathrm{crit} \delta_c}{(r/r_s)\left(1 + r/r_s\right)^2}
-\end{equation}
-
-\begin{equation}
-    \Sigma_\mathrm{NFW}(R) = \frac{2 \rho_\mathrm{crit} \delta_c r_s}{(R/r_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(R/r_s)^2 - 1}} \right) \arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right)
-\end{equation}
-[Bartelmann 2001]
-
-\begin{equation}
-    \overline{\Sigma}_\mathrm{NFW}(R) = \frac{4 \rho_\mathrm{crit} \delta_c r_s}{(R/r_s)^2} \left(
-        \frac{2}{\sqrt{(R/r_s)^2 - 1}} ~\arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) + \ln{\left(\frac{R/r_s}{2}\right)}
-    \right)
-\end{equation}
-
-\begin{equation}
-    \gamma(R) =
-\end{equation}
-
-We switch the dependence to $M_{200}$ and $c$ with:
-
-\begin{equation}
-    \delta_c = \frac{200}{3} \frac{c^3}{\ln(1 + c) - c/(1 + c)}
-\end{equation}
-
-\begin{equation}
-    r_s = \frac{1}{c} \left(\frac{3M_{200}}{800\pi \rho_\mathrm{crit}}\right)^\frac{1}{3}
-\end{equation}
-
 \subsection{Cored Isothermal Sphere Profile}
 
-\begin{equation}
-    \rho_\mathrm{iso}(r) = \frac{\sigma^2}{2\pi G (r^2 + {r_c}^2)}
-\end{equation}
+\[\rho_\mathrm{iso}(r) = \frac{\sigma^2}{2\pi G (r^2 + {r_c}^2)}\]
 
-\begin{equation}
-    \Sigma_\mathrm{iso}(R) = \frac{\sigma^2}{2 G \sqrt{R^2 + {r_c}^2}}
-\end{equation}
+\[\Sigma_\mathrm{iso}(R) = \frac{\sigma^2}{2 G \sqrt{R^2 + {r_c}^2}}\]
 
-\begin{equation}
-    \overline{\Sigma}_\mathrm{iso}(R) = \frac{\sigma^2 \left(\sqrt{R^2 + {r_c}^2} - r_c \right)}{G R^2}
-\end{equation}
+\[\overline{\Sigma}_\mathrm{iso}(R) = \frac{\sigma^2 \left(\sqrt{R^2 + {r_c}^2} - r_c \right)}{G R^2}\]
 
-\begin{equation}
-    \gamma(R) = \frac{\sigma^2 \left(\sqrt{R^2 + {r_c}^2} - r_c \right)}{\Sigma_\mathrm{crit} G R^2} - \frac{\sigma^2}{2 \Sigma_\mathrm{crit} G \sqrt{R^2 + {r_c}^2}}
-\end{equation}
+In terms of angles:
+
+\[\Sigma_\mathrm{iso}(\theta) = \frac{\sigma^2}{2 G D_L \sqrt{\theta^2 + {\theta_c}^2}}\]
+
+\[\overline{\Sigma}_\mathrm{iso}(\theta) = \frac{\sigma^2 \left(\sqrt{\theta^2 + {\theta_c}^2} - \theta_c \right)}{G D_L \theta^2}\]
+
+\[\gamma_\mathrm{iso}(\theta) = \frac{\sigma^2 \left(\sqrt{\theta^2 + {\theta_c}^2} - \theta_c \right)}{\Sigma_\mathrm{crit} G D_L \theta^2} - \frac{\sigma^2}{2 \Sigma_\mathrm{crit} G D_L \sqrt{\theta^2 + {\theta_c}^2}}\]
 
@@
 
-\begin{equation}
-    r_{200} = \left( \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}} \right)^{1/3}
-\end{equation}
-
-\begin{equation}
-    \sigma^2 = \frac{G M_{200}}{2 \left(
+\[\sigma^2 = \frac{G M_{200}}{2 \left(
     \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}}
@@
     \right)
-    \right)}
-\end{equation}
+\right)}\]
+\[\sigma^2 = \frac{G M_{200}}{2 \left(
+    \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}}
+    - D_L \theta_c \arctan \left(
+        \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit} {D_L}^3 {\theta_c}^3}
+    \right)
+\right)}\]
 
-$M_{200}$ is defined as:
-\begin{equation}
-    M_{200} = M_{enc}(r_{200}) = 200 \rho_\mathrm{crit} \frac{4}{3} \pi r_{200}^3
-\end{equation}
+This is derived from the definition of $M_{200}$:
+
+\[M_{200} = M_{enc}(r_{200}) = 200 \rho_\mathrm{crit} \frac{4}{3} \pi {r_{200}}^3\]
+\[r_{200} = \left( \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}} \right)^{1/3}\]
+
+Ellipticity equations are very ugly but trivial to calculate from the shear.
+
+\subsection{Navarro-Frenk-White (NFW) Profile}
+
+\[\rho_\mathrm{NFW}(r) = \frac{\rho_\mathrm{crit} \delta_C}{(r/r_s)\left(1 + r/r_s\right)^2}\]
+
+\[\Sigma_\mathrm{NFW}(R) = \frac{2 \rho_\mathrm{crit} \delta_C r_s}{(R/r_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(R/r_s)^2 - 1}} \right) \arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right)\]
+[Bartelmann 2001]
+
+\[\overline{\Sigma}_\mathrm{NFW}(R) = \frac{4 \rho_\mathrm{crit} \delta_C r_s}{(R/r_s)^2} \left(
+    \frac{2}{\sqrt{(R/r_s)^2 - 1}} ~\arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) + \ln{\left(\frac{R/r_s}{2}\right)}
+\right)\]
+
+In terms of angles:
+
+\[\Sigma_\mathrm{NFW}(\theta) = \frac{2 \rho_\mathrm{crit} \delta_C D_L \theta_s}{(\theta/\theta_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(\theta/\theta_s)^2 - 1}} \right) \arctan\left(\sqrt{\frac{\theta/\theta_s - 1}{\theta/\theta_s + 1}} \right)\]
+
+\[\overline{\Sigma}_\mathrm{NFW}(\theta) = \frac{4 \rho_\mathrm{crit} \delta_C D_L \theta_s}{(\theta/\theta_s)^2} \left(
+    \frac{2}{\sqrt{(\theta/\theta_s)^2 - 1}} ~\arctan\left(\sqrt{\frac{\theta/\theta_s - 1}{\theta/\theta_s + 1}} \right) + \ln{\left(\frac{\theta/\theta_s}{2}\right)}
+\right)\]
+
+\[\gamma_\mathrm{NFW}(\theta) = \frac{\overline{\Sigma}_\mathrm{NFW}(\theta) - \Sigma_\mathrm{NFW}(\theta)}{\Sigma_\mathrm{crit}} \]
+
+Can calculate ellipticities from tangential shear.
+
+We switch the dependence to $M_{200}$ and $C$ with:
+
+\[\delta_C = \frac{200}{3} \frac{C^3}{\ln(1 + C) - C/(1 + C)}\]
+
+\[r_s = \frac{1}{C} \left(\frac{3M_{200}}{800\pi \rho_\mathrm{crit}}\right)^\frac{1}{3}\]
+
+\[C = \frac{r_{200}}{r_s}\]
+
+\section{Methods}
 
@@
 
+Fake data:
 N sets of e1, e2, theta1, theta2
@@
 $z_S = 1$
-$M_halo = 10^15$ solar masses
+$M_{halo} = 10^15$ solar masses
 instrinsic ellipticity from gaussian with width 0.2
 
-\section{Methods}
-
 \end{document}

### 2018-04-18 lensing.py
lensing.py is now much more legitimate

@@ -13,7 +13,7 @@ c = const.c
 G = const.G
 H0 = cosmology.default_cosmology.get().H(0)
 RHO_CRIT = 3 * H0**2 / (8 * np.pi * G)
-
+u.set_enabled_equivalencies(u.dimensionless_angles())
 
 def SIGMA_CRIT(DS, DL):
     DSL = DS - DL
@@ -22,94 +22,109 @@ def SIGMA_CRIT(DS, DL):
 
 class NFWHalo:
 
-    def __init__(self, M200, c_param, DL):
+    def __init__(self, M200, C, DL):
         self.M200 = M200
-        self.c = c_param     #changed variable name for clarification
-        self.delta_c = (200/3) * c_param**3 / (np.log(1+c_param) - c_param/(1+c_param))
-        self.rs = 1/c_param * ((3 * M200) / (800 * np.pi * RHO_CRIT))**(1/3)
+        self.C = C
+        self.delta_c = (200/3) * C**3 / (np.log(1+C) - C/(1+C))
+        r200 = ((3 * M200) / (800 * np.pi * RHO_CRIT))**(1/3)
+        self.rs = r200/C
         self.DL = DL
 
 
 class IsothermalHalo:
 
-    def __init__(self, sigma, rc, DL):
-        self.sigma = sigma
+    def __init__(self, M200, rc, DL):
+        self.M200 = M200
         self.rc = rc
         self.DL = DL
+        self.Tc = rc/DL * u.rad
+        r200 = ((3 * M200) / (800 * np.pi * RHO_CRIT))**(1/3)
+        self.sigmaSquared = M200 * G / (2 * (r200 - rc * np.arctan(r200/rc)))
 
-    def surfaceDensity(self, R):
-        return self.sigma**2 / (2 * G * np.sqrt(R**2 + self.rc**2))
+    def surfaceDensity(self, T):
+        # Surface density at angle T
+        return self.sigmaSquared / (2 * G * self.DL * np.sqrt(T**2 + self.Tc**2))
 
-    def averageSurfaceDensity(self, R):
-        return self.sigma**2 * (np.sqrt(R**2 + self.rc**2) - self.rc) / (G * R**2)
+    def averageSurfaceDensity(self, T):
+        # Average surface density at angle T
+        return self.sigmaSquared * (np.sqrt(T**2 + self.Tc**2) - self.Tc) / (G * self.DL * T**2)
 
[…]

### 2018-04-22 lensing.py
Fixed an error in the NFW sigma formula, added Halo base class to reduce code repetition

@@ -20,34 +20,11 @@ def SIGMA_CRIT(DS, DL):
     return c**2 / (4 * np.pi * G) * (DS / (DSL * DL))
 
 
-class NFWHalo:
+class Halo:
 
-    def __init__(self, M200, C, DL):
+    def __init__(self, M200, DL):
         self.M200 = M200
-        self.C = C
-        self.delta_c = (200/3) * C**3 / (np.log(1+C) - C/(1+C))
-        r200 = ((3 * M200) / (800 * np.pi * RHO_CRIT))**(1/3)
-        self.rs = r200/C
         self.DL = DL
-
-
-class IsothermalHalo:
-
-    def __init__(self, M200, rc, DL):
-        self.M200 = M200
-        self.rc = rc
-        self.DL = DL
-        self.Tc = rc/DL * u.rad
-        r200 = ((3 * M200) / (800 * np.pi * RHO_CRIT))**(1/3)
-        self.sigmaSquared = M200 * G / (2 * (r200 - rc * np.arctan(r200/rc)))
-
-    def surfaceDensity(self, T):
-        # Surface density at angle T
-        return self.sigmaSquared / (2 * G * self.DL * np.sqrt(T**2 + self.Tc**2))
-
-    def averageSurfaceDensity(self, T):
-        # Average surface density at angle T
-        return self.sigmaSquared * (np.sqrt(T**2 + self.Tc**2) - self.Tc) / (G * self.DL * T**2)
 
     def shear(self, T, DS):
         # Tangential shear at angle T for object at distance DS
@@ -72,6 +49,67 @@ class IsothermalHalo:
         e1 = -e*np.cos(2*phi)
         e2 = -e*np.sin(2*phi)
         return LensedBackgroundGalaxy(Tx, Ty, galaxy.a, e1, e2, galaxy.DS)
+
+    def plot(self, start, stop, step, DS):
+        theta = np.linspace(start, stop, step)*u.arcsec
+        epsilon = np.array([self.ellipticity(t, DS).to_value("") for t in theta])
+        gamma = np.array([self.shear(t, DS).to_value("") for t in theta])
[…]

### 2018-04-22 lensing.py
Added complex sqrt function

@@ -5,6 +5,7 @@ import astropy.cosmology as cosmology
 from astropy.visualization import astropy_mpl_style
 import astropy.units as u
 import astropy.constants as const
+import cmath.sqrt as csqrt
 
 plt.style.use(astropy_mpl_style)
 
@@ -77,19 +78,18 @@ class NFWHalo(Halo):
         r200 = ((3 * M200) / (800 * np.pi * RHO_CRIT))**(1/3)
         self.rs = r200/C
         self.Ts = self.rs/DL * u.rad
-        self.csqrt = np.lib.scimath.sqrt
 
     def surfaceDensity(self, T):
         # Surface density at angle T
         x = T/self.Ts
-        sigma = 2*RHO_CRIT * self.delta_c * self.rs / (x**2 - 1) * (1 - 2 / self.csqrt(x**2 - 1) * np.arctan(self.csqrt((x-1)/(x+1))))
+        sigma = 2*RHO_CRIT * self.delta_c * self.rs / (x**2 - 1) * (1 - 2 / csqrt(x**2 - 1) * np.arctan(csqrt((x-1)/(x+1))))
         if sigma.imag != 0: print(sigma.imag)
         return sigma.real
 
     def averageSurfaceDensity(self, T):
         # Average surface density at angle T
         x = T/self.Ts
-        sigma_bar = 4*RHO_CRIT * self.delta_c * self.rs / x**2 * (2 / self.csqrt(x**2 - 1) * np.arctan(self.csqrt((x-1)/(x+1))) + np.log(x/2))
+        sigma_bar = 4*RHO_CRIT * self.delta_c * self.rs / x**2 * (2 / csqrt(x**2 - 1) * np.arctan(csqrt((x-1)/(x+1))) + np.log(x/2))
         if sigma_bar.imag != 0: print(sigma_bar.imag)
         return sigma_bar.real
 
@@ -153,7 +153,7 @@ halo = IsothermalHalo(
 
 halo2 = NFWHalo(
     M200=1e15*u.solMass,
-    C=20,
+    C=10,
     DL=1*u.Gpc)
 
 backgroundGalaxies = [BackgroundGalaxy(
@@ -164,17 +164,18 @@ backgroundGalaxies = [BackgroundGalaxy(
     a=1,
[…]

### 2018-04-22 lensing.py
Cleaned up and modularized things

@@ -5,7 +5,7 @@ import astropy.cosmology as cosmology
 from astropy.visualization import astropy_mpl_style
 import astropy.units as u
 import astropy.constants as const
-import cmath.sqrt as csqrt
+from cmath import sqrt as csqrt
 
 plt.style.use(astropy_mpl_style)
 
@@ -102,6 +102,7 @@ class IsothermalHalo(Halo):
         self.Tc = rc/DL * u.rad
         r200 = ((3 * M200) / (800 * np.pi * RHO_CRIT))**(1/3)
         self.sigmaSquared = M200 * G / (2 * (r200 - rc * np.arctan(r200/rc)))
+        self.T0 = lambda DS: 4*np.pi*halo_iso.sigmaSquared / c**2 * (DS - halo_iso.DL)/(DS)
 
     def surfaceDensity(self, T):
         # Surface density at angle T
@@ -143,52 +144,47 @@ class LensedBackgroundGalaxy:
                        angle=self.phi.to_value(u.degree))
 
 
-# if __name__ == '__main__':
-v = 100
 
-halo = IsothermalHalo(
-    M200=1e15*u.solMass,
-    rc=10*u.kpc,
-    DL=1*u.Gpc)
-
-halo2 = NFWHalo(
-    M200=1e15*u.solMass,
-    C=10,
-    DL=1*u.Gpc)
-
-backgroundGalaxies = [BackgroundGalaxy(
-    Bx=(v*np.random.rand()-v/2)*u.arcsec,
-    By=(v*np.random.rand()-v/2)*u.arcsec,
-    e1=0,
-    e2=0,
-    a=1,
-    DS=3*u.Gpc) for i in range(1000)]
-
-halo.plot(0.0001, 100, 1000, 3*u.Gpc)
-halo2.plot(0.0001, 100, 1000, 3*u.Gpc)
-
-fig = plt.figure(dpi=100)
-ax = fig.add_subplot(111, aspect="equal")
-ax.set_xlim(-v/2,v/2)
-ax.set_ylim(-v/2,v/2)
-for gal in backgroundGalaxies:
-    lensedGal = halo.lense(gal)
-    lensedGalEllipse = lensedGal.ellipse()
-    lensedGalEllipse.set_facecolor(np.random.rand(3))
-    ax.add_artist(lensedGalEllipse)
-plt.show()
+def make_lensing_image(halo, backgroundGalaxies, v):
[…]

### 2018-04-22 analysis.py
Added pretty much complete analysis code

@@ -1,0 +1,68 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import astropy.cosmology as cosmology
+import astropy.units as u
+from lensing import NFWHalo, IsothermalHalo
+from scipy.optimize import curve_fit
+from scipy.stats import binned_statistic
+
+
+# data generation
+halo_nfw = NFWHalo(
+    M200=1e15*u.solMass,
+    C=10,
+    DL=1*u.Gpc)
+
+from lensing import BackgroundGalaxy
+v=100
+backgroundGalaxies = [BackgroundGalaxy(
+    Bx=(v*np.random.rand()-v/2)*u.arcsec,
+    By=(v*np.random.rand()-v/2)*u.arcsec,
+    e1=0,
+    e2=0,
+    a=1,
+    DS=3*u.Gpc) for i in range(1000)]
+
+lensedBackgroundGalaxies = []
+for gal in backgroundGalaxies:
+    lensedBackgroundGalaxies.append(halo_nfw.lense(gal))
+
+theta_x = np.array([lgal.Tx.to_value(u.arcsec) for lgal in lensedBackgroundGalaxies]) * u.arcsec
+theta_y = np.array([lgal.Ty.to_value(u.arcsec) for lgal in lensedBackgroundGalaxies]) * u.arcsec
+e1 = np.array([lgal.e1.to_value("") for lgal in lensedBackgroundGalaxies])
+e2 = np.array([lgal.e2.to_value("") for lgal in lensedBackgroundGalaxies])
+phi = np.array([lgal.phi.to_value(u.rad) for lgal in lensedBackgroundGalaxies])
+
+# Assume we have a dataset of N galaxies with positions (theta_x, theta_y) and ellipticities (e1, e2)
+# Assumer they all have same DS and DL is known
+DS = 3*u.Gpc
+DL = 1*u.Gpc
+# Assume these are numpy arrays of length N
+
+theta = np.sqrt(theta_x**2 + theta_y**2)
+epsilon = -e1*np.cos(2*phi) - e2*np.sin(2*phi)
+
+# Bin into annuli and calculate mean and standard deviation
+theta_bin_edges = np.linspace(1, 70, 30)
+epsilon_mean, bin_edges, binnumber = binned_statistic(theta, epsilon, statistic="mean", bins=theta_bin_edges)
[…]

### 2018-04-22 lensing.py

@@ -35,7 +35,7 @@ class Halo:
         # Magnitude of ellipticity at angle T for object at distance DS
         convergence = self.surfaceDensity(T) / SIGMA_CRIT(DS, self.DL)
         reducedShear = self.shear(T, DS) / (1 - convergence)
-        return 2 * reducedShear / (1 + reducedShear**2)
+        return (2 * reducedShear / (1 + reducedShear**2)).to_value("")
 
     def deflection(self, Bx, By, DS):
         # Gives the image angle theta (T) that an object at source angle beta (B) and distance DS is deflected to

### 2018-04-22 analysis.py
Fixed issue with units and arrays

@@ -48,7 +48,6 @@ epsilon_mean, bin_edges, binnumber = binned_statistic(theta, epsilon, statistic=
 epsilon_sigma, bin_edges, binnumber = binned_statistic(theta, epsilon, statistic=np.std, bins=theta_bin_edges)
 theta_bin_centers = theta_bin_edges[:-1] + (theta_bin_edges[1] - theta_bin_edges[0])/2
 
-
 # FITTING
 def nfw_ellipticity(theta, M200, C):
     halo = NFWHalo(M200*u.solMass, C, DL)
@@ -62,7 +61,10 @@ BOUNDS = [[0,0], [np.inf, np.inf]]
 optimalNFWParams, covariance = curve_fit(nfw_ellipticity, theta_bin_centers, epsilon_mean, p0=[1e14, 10], bounds=BOUNDS, sigma=epsilon_sigma)
 optimalIsoParams, covariance = curve_fit(iso_ellipticity, theta_bin_centers, epsilon_mean, p0=[1e14, 10], bounds=BOUNDS, sigma=epsilon_sigma)
 
-plt.plot(theta_bin_centers, epsilon_mean)
+plt.figure()
 plt.plot(theta_bin_centers, nfw_ellipticity(theta_bin_centers, 1e15,10))
+plt.plot(theta_bin_centers, epsilon_mean)
 plt.plot(theta_bin_centers, nfw_ellipticity(theta_bin_centers, *optimalNFWParams))
 plt.plot(theta_bin_centers, iso_ellipticity(theta_bin_centers, *optimalIsoParams))
+plt.legend(["original", "binned data", "nfw fit", "isothermal fit"])
+plt.show()

### 2018-04-22 lensing.py

@@ -29,7 +29,7 @@ class Halo:
 
     def shear(self, T, DS):
         # Tangential shear at angle T for object at distance DS
-        return (self.averageSurfaceDensity(T) - self.surfaceDensity(T)) / SIGMA_CRIT(DS, self.DL)
+        return ((self.averageSurfaceDensity(T) - self.surfaceDensity(T)) / SIGMA_CRIT(DS, self.DL)).to_value("")
 
     def ellipticity(self, T, DS):
         # Magnitude of ellipticity at angle T for object at distance DS
@@ -53,8 +53,8 @@ class Halo:
 
     def plot(self, start, stop, step, DS):
         theta = np.linspace(start, stop, step)*u.arcsec
-        epsilon = np.array([self.ellipticity(t, DS).to_value("") for t in theta])
-        gamma = np.array([self.shear(t, DS).to_value("") for t in theta])
+        epsilon = np.array([self.ellipticity(t, DS) for t in theta])
+        gamma = np.array([self.shear(t, DS) for t in theta])
         kappa = np.array([(self.surfaceDensity(t) / SIGMA_CRIT(DS, self.DL)).to_value("") for t in theta])
         mu = 1/((1-kappa)**2 - gamma**2)
         plt.figure()

### 2018-04-22 datagenerator.py
modified data generator and generated data file

@@ -31,17 +31,17 @@ dl = 1*u.Gpc
 datafile = open('output1.txt','w')
 nfw_1 = NFWHalo(M200_0,c_param,dl)
 backgroundGalaxies = [BackgroundGalaxy(
-    beta_x=(100*np.random.rand()-50)*u.arcsec,
-    beta_y=(100*np.random.rand()-50)*u.arcsec,
+    Bx=(100*np.random.rand()-50)*u.arcsec,
+    By=(100*np.random.rand()-50)*u.arcsec,
     e1=0,
     e2=0,
     a=1*u.arcsec,
     DS=10*u.Gpc) for i in range(300)]
 for i in range(0,len(backgroundGalaxies)):
     newGalx = nfw_1.lense(backgroundGalaxies[i])
-    datafile.write(newGalx.theta_x,"\t",newGalx.theta_y,"\t",newGalx.e1,"\t",newGalx.e2,"\t\n")
+    datafile.write(str(newGalx.Tx)+"\t"+str(newGalx.Ty)+"\t"+str(newGalx.e1)+"\t"+str(newGalx.e2)+"\t\n")
 
-#Isothermal Profile lensing will be added once the paramaters are modified
+#Isothermal Profile lensing will be added once the parameters are modified
 #to be identical to those of NFW
 
 datafile.close()

### 2018-04-22 datagenerator.py
added comments

@@ -30,6 +30,9 @@ dl = 1*u.Gpc
 
 datafile = open('output1.txt','w')
 nfw_1 = NFWHalo(M200_0,c_param,dl)
+
+#Sample NFW lensed galaxy data made with rand().
+#More deliberate placing of galaxies can be done if found necessary
 backgroundGalaxies = [BackgroundGalaxy(
     Bx=(100*np.random.rand()-50)*u.arcsec,
     By=(100*np.random.rand()-50)*u.arcsec,

### 2018-04-22 analysis.py
Produces analysis for data far from halo - now with intrinsic ellipticity!

@@ -2,30 +2,28 @@ import numpy as np
 import matplotlib.pyplot as plt
 import astropy.cosmology as cosmology
 import astropy.units as u
-from lensing import NFWHalo, IsothermalHalo
 from scipy.optimize import curve_fit
 from scipy.stats import binned_statistic
+from lensing import *
 
+### DATA GENERATION ###
+galaxyNumberDensity = 50/u.arcmin**2
+viewSize = 1000*u.arcsec
+Ngal = round((viewSize**2 * galaxyNumberDensity).to_value(""))
 
-# data generation
-halo_nfw = NFWHalo(
+lensHalo = NFWHalo(
     M200=1e15*u.solMass,
     C=10,
     DL=1*u.Gpc)
 
-from lensing import BackgroundGalaxy
-v=100
 backgroundGalaxies = [BackgroundGalaxy(
-    Bx=(v*np.random.rand()-v/2)*u.arcsec,
-    By=(v*np.random.rand()-v/2)*u.arcsec,
-    e1=0,
-    e2=0,
-    a=1,
-    DS=3*u.Gpc) for i in range(1000)]
+    Bx=(viewSize*np.random.rand() - viewSize/2),
+    By=(viewSize*np.random.rand() - viewSize/2),
+    e1=np.random.normal(0, 0.2),
+    e2=np.random.normal(0, 0.2),
+    DS=3*u.Gpc) for i in range(Ngal)]
 
-lensedBackgroundGalaxies = []
-for gal in backgroundGalaxies:
-    lensedBackgroundGalaxies.append(halo_nfw.lense(gal))
+lensedBackgroundGalaxies = [lensHalo.lense(gal) for gal in backgroundGalaxies]
 
 theta_x = np.array([lgal.Tx.to_value(u.arcsec) for lgal in lensedBackgroundGalaxies]) * u.arcsec
 theta_y = np.array([lgal.Ty.to_value(u.arcsec) for lgal in lensedBackgroundGalaxies]) * u.arcsec
@@ -33,6 +31,8 @@ e1 = np.array([lgal.e1.to_value("") for lgal in lensedBackgroundGalaxies])
 e2 = np.array([lgal.e2.to_value("") for lgal in lensedBackgroundGalaxies])
 phi = np.array([lgal.phi.to_value(u.rad) for lgal in lensedBackgroundGalaxies])
 
+
+### ANALYSIS ###
[…]

### 2018-04-22 lensing.py

@@ -8,18 +8,36 @@ import astropy.constants as const
 from cmath import sqrt as csqrt
 
 plt.style.use(astropy_mpl_style)
+plt.rcParams["figure.dpi"] = 150
 
-#Define constants
+### CONSTANTS ###
 c = const.c
 G = const.G
 H0 = cosmology.default_cosmology.get().H(0)
 RHO_CRIT = 3 * H0**2 / (8 * np.pi * G)
-u.set_enabled_equivalencies(u.dimensionless_angles())
+u.set_enabled_equivalencies(u.dimensionless_angles()) # allow angles to be dimensionless
+
+
+### USEFUL FUNCTIONS ###
 
 def SIGMA_CRIT(DS, DL):
     DSL = DS - DL
     return c**2 / (4 * np.pi * G) * (DS / (DSL * DL))
 
+def lensingImage(halo, backgroundGalaxies, v):
+    fig = plt.figure()
+    ax = fig.add_subplot(111, aspect="equal")
+    ax.set_xlim(-v/2,v/2)
+    ax.set_ylim(-v/2,v/2)
+    for gal in backgroundGalaxies:
+        lensedGal = halo.lense(gal)
+        lensedGalEllipse = lensedGal.ellipse(1)
+        lensedGalEllipse.set_facecolor(np.random.rand(3))
+        ax.add_artist(lensedGalEllipse)
+    return plt.show()
+
+
+### GALAXY/HALO OBJECTS ###
 
 class Halo:
 
@@ -47,9 +65,9 @@ class Halo:
         T = np.sqrt(Tx**2 + Ty**2)
         phi = np.arctan2(Ty, Tx)
         e = self.ellipticity(T, galaxy.DS)
-        e1 = -e*np.cos(2*phi)
-        e2 = -e*np.sin(2*phi)
-        return LensedBackgroundGalaxy(Tx, Ty, galaxy.a, e1, e2, galaxy.DS)
+        e1 = galaxy.e1 - e*np.cos(2*phi) # TODO: how do ellipticities add?
+        e2 = galaxy.e2 - e*np.sin(2*phi)
+        return LensedBackgroundGalaxy(Tx, Ty, e1, e2, galaxy.DS)
 
     def plot(self, start, stop, step, DS):
         theta = np.linspace(start, stop, step)*u.arcsec
@@ -115,10 +133,9 @@ class IsothermalHalo(Halo):
 
 class BackgroundGalaxy:
 
[…]

### 2018-04-22 analysis.py
Added extra comments

@@ -33,12 +33,14 @@ phi = np.array([lgal.phi.to_value(u.rad) for lgal in lensedBackgroundGalaxies])
 
 
 ### ANALYSIS ###
+
 # Assume we have a dataset of N galaxies with positions (theta_x, theta_y) and ellipticities (e1, e2)
 # Assumer they all have same DS and DL is known
 DS = 3*u.Gpc
 DL = 1*u.Gpc
 # Assume these are numpy arrays of length N
 
+# Calculate radial position theta and magnitude of ellipticity epsilon
 theta = np.sqrt(theta_x**2 + theta_y**2)
 epsilon = -e1*np.cos(2*phi) - e2*np.sin(2*phi)
 
@@ -48,7 +50,9 @@ epsilon_mean, bin_edges, binnumber = binned_statistic(theta, epsilon, statistic=
 epsilon_sigma, bin_edges, binnumber = binned_statistic(theta, epsilon, statistic=np.std, bins=theta_bin_edges)
 theta_bin_centers = theta_bin_edges[:-1] + (theta_bin_edges[1] - theta_bin_edges[0])/2
 
-# FITTING
+
+### FITTING ###
+
 def nfw_ellipticity(theta, M200, C):
     halo = NFWHalo(M200*u.solMass, C, DL)
     return np.array([halo.ellipticity(t*u.arcsec, DS) for t in theta])
@@ -58,14 +62,16 @@ def iso_ellipticity(theta, M200, rc):
     return np.array([halo.ellipticity(t*u.arcsec, DS) for t in theta])
 
 BOUNDS = [[0,0], [np.inf, np.inf]]
-optimalNFWParams, covariance = curve_fit(nfw_ellipticity, theta_bin_centers, epsilon_mean, p0=[1e14, 10], bounds=BOUNDS, sigma=epsilon_sigma)
-optimalIsoParams, covariance = curve_fit(iso_ellipticity, theta_bin_centers, epsilon_mean, p0=[1e14, 10], bounds=BOUNDS, sigma=epsilon_sigma)
+optimalNFWParams, covariance = curve_fit(nfw_ellipticity, theta_bin_centers, epsilon_mean, p0=[1e16, 20], bounds=BOUNDS, sigma=epsilon_sigma)
[…]

### 2018-04-22 lensing.py

@@ -8,30 +8,33 @@ import astropy.constants as const
 from cmath import sqrt as csqrt
 
 plt.style.use(astropy_mpl_style)
-plt.rcParams["figure.dpi"] = 150
+plt.rcParams["figure.dpi"] = 100
 
 ### CONSTANTS ###
 c = const.c
 G = const.G
 H0 = cosmology.default_cosmology.get().H(0)
-RHO_CRIT = 3 * H0**2 / (8 * np.pi * G)
+RHO_CRIT = 3 * H0**2 / (8 * np.pi * G) # only use rho_crit at current time
 u.set_enabled_equivalencies(u.dimensionless_angles()) # allow angles to be dimensionless
 
 
 ### USEFUL FUNCTIONS ###
 
 def SIGMA_CRIT(DS, DL):
+    # Critical surface density for lens at distance DL and source at distance DS
     DSL = DS - DL
     return c**2 / (4 * np.pi * G) * (DS / (DSL * DL))
 
-def lensingImage(halo, backgroundGalaxies, v):
+def lensingImage(halo, backgroundGalaxies, v, a):
+    # Produce a mock lensing image with a halo and a population of background galaxies
+    # v is the view width and a is the size of galaxies
     fig = plt.figure()
     ax = fig.add_subplot(111, aspect="equal")
     ax.set_xlim(-v/2,v/2)
     ax.set_ylim(-v/2,v/2)
     for gal in backgroundGalaxies:
         lensedGal = halo.lense(gal)
-        lensedGalEllipse = lensedGal.ellipse(1)
+        lensedGalEllipse = lensedGal.ellipse(a)
         lensedGalEllipse.set_facecolor(np.random.rand(3))
         ax.add_artist(lensedGalEllipse)
     return plt.show()
@@ -70,6 +73,7 @@ class Halo:
         return LensedBackgroundGalaxy(Tx, Ty, e1, e2, galaxy.DS)
 
     def plot(self, start, stop, step, DS):
+        # Plot the shear, ellipticity, convergence, and magnification for the halo
         theta = np.linspace(start, stop, step)*u.arcsec
         epsilon = np.array([self.ellipticity(t, DS) for t in theta])
         gamma = np.array([self.shear(t, DS) for t in theta])

### 2018-04-22 analysis.py
Save out data for analysis in Mathematica

@@ -49,6 +49,7 @@ theta_bin_edges = np.linspace(50, 700, 40) # arcsec
 epsilon_mean, bin_edges, binnumber = binned_statistic(theta, epsilon, statistic="mean", bins=theta_bin_edges)
 epsilon_sigma, bin_edges, binnumber = binned_statistic(theta, epsilon, statistic=np.std, bins=theta_bin_edges)
 theta_bin_centers = theta_bin_edges[:-1] + (theta_bin_edges[1] - theta_bin_edges[0])/2
+np.savetxt("data.csv", np.stack([theta_bin_centers, epsilon_mean, epsilon_sigma], 1), delimiter=", ")
 
 
 ### FITTING ###

### 2018-04-28 lensing.py
Added mathematica notebook for fitting

@@ -72,7 +72,7 @@ class Halo:
         e2 = galaxy.e2 - e*np.sin(2*phi)
         return LensedBackgroundGalaxy(Tx, Ty, e1, e2, galaxy.DS)
 
-    def plot(self, start, stop, step, DS):
+    def plotProperties(self, start, stop, step, DS):
         # Plot the shear, ellipticity, convergence, and magnification for the halo
         theta = np.linspace(start, stop, step)*u.arcsec
         epsilon = np.array([self.ellipticity(t, DS) for t in theta])
@@ -180,11 +180,11 @@ if __name__ == '__main__':
         C=10,
         DL=1*u.Gpc)
 
-    halo_iso.plot(0.0001, v, 500, 3*u.Gpc)
+    halo_iso.plotProperties(0.0001, v, 500, 3*u.Gpc)
     print("theta_c:", halo_iso.Tc.to(u.arcsec))
     print("theta_0:", halo_iso.T0(3*u.Gpc).to(u.arcsec))
 
-    halo_nfw.plot(0.0001, v, 500, 3*u.Gpc)
+    halo_nfw.plotProperties(0.0001, v, 500, 3*u.Gpc)
     print("theta_s:", halo_nfw.Ts.to(u.arcsec))
 
     backgroundGalaxies = [BackgroundGalaxy(

### 2018-04-29 paper.tex
lensing.py is now much more legitimate
Fixed an error in the NFW sigma formula, added Halo base class to reduce code repetition
Added pretty much complete analysis code
Data exported with correct uncertainty on the mean

@@
 \begin{document}
-\title{Distinguishing NFW and Isothermal Density Profiles with Gravitational Lensing}
+\title{Distinguishing NFW and Isothermal Density Profiles with Weak Gravitational Lensing}
 \author{}
@@
 \begin{abstract}
-We attempt to distinguish NFW and cored isothermal density profiles using weak gravitational lensing shear.
+We examine the feasibility of distinguishing NFW and cored isothermal density profiles using weak gravitational lensing shear.
 \end{abstract}
@@
 
-\[\sigma^2 = \frac{G M_{200}}{2 \left(
-    \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}}
-    - r_c \arctan \left(
-        \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit} {r_c}^3}
-    \right)
-\right)}\]
-\[\sigma^2 = \frac{G M_{200}}{2 \left(
-    \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}}
-    - D_L \theta_c \arctan \left(
-        \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit} {D_L}^3 {\theta_c}^3}
-    \right)
-\right)}\]
+\[\sigma^2 = \frac{M_{200} G}{2 \left( r_{200} - r_c \arctan{\left(\frac{r_{200}}{r_c}\right)} \right)}\]
 
@@
 
-\[M_{200} = M_{enc}(r_{200}) = 200 \rho_\mathrm{crit} \frac{4}{3} \pi {r_{200}}^3\]
+\[M_{200} = 200 \rho_\mathrm{crit} \frac{4}{3} \pi {r_{200}}^3\]
+\[M_{200} = M_\mathrm{enc}(r_{200}) = \frac{2 \sigma^2}{G} \left( r_{200} - r_c \arctan{\left(\frac{r_{200}}{r_c}\right)} \right)\]
 \[r_{200} = \left( \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}} \right)^{1/3}\]
@@
 
-\[\Sigma_\mathrm{NFW}(R) = \frac{2 \rho_\mathrm{crit} \delta_C r_s}{(R/r_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(R/r_s)^2 - 1}} \right) \arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right)\]
+\[\Sigma_\mathrm{NFW}(R) = \frac{2 \rho_\mathrm{crit} \delta_C r_s}{(R/r_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(R/r_s)^2 - 1}}  \arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) \right)\]
 [Bartelmann 2001]
@@
 
-\[\Sigma_\mathrm{NFW}(\theta) = \frac{2 \rho_\mathrm{crit} \delta_C D_L \theta_s}{(\theta/\theta_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(\theta/\theta_s)^2 - 1}} \right) \arctan\left(\sqrt{\frac{\theta/\theta_s - 1}{\theta/\theta_s + 1}} \right)\]
+\[\Sigma_\mathrm{NFW}(\theta) = \frac{2 \rho_\mathrm{crit} \delta_C D_L \theta_s}{(\theta/\theta_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(\theta/\theta_s)^2 - 1}} \arctan\left(\sqrt{\frac{\theta/\theta_s - 1}{\theta/\theta_s + 1}} \right) \right)\]
 
@@
 \[\delta_C = \frac{200}{3} \frac{C^3}{\ln(1 + C) - C/(1 + C)}\]
-
-\[r_s = \frac{1}{C} \left(\frac{3M_{200}}{800\pi \rho_\mathrm{crit}}\right)^\frac{1}{3}\]
-
+\[r_s = \frac{r_{200}}{C}\]
+\[r_{200} = \left( \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}} \right)^{1/3}\]
 \[C = \frac{r_{200}}{r_s}\]
@@
 
+Assume same DS since this can be determined by redshift anyway
+
+estimating ellipticity has well-documented issues [cite] due to noise and PSF
+
 \end{document}

### 2018-04-29 analysis.py

@@ -45,11 +45,12 @@ theta = np.sqrt(theta_x**2 + theta_y**2)
 epsilon = -e1*np.cos(2*phi) - e2*np.sin(2*phi)
 
 # Bin into annuli and calculate mean and standard deviation
-theta_bin_edges = np.linspace(50, 700, 40) # arcsec
+theta_bin_edges = np.linspace(100*u.arcsec, viewSize/np.sqrt(2), 40)
 epsilon_mean, bin_edges, binnumber = binned_statistic(theta, epsilon, statistic="mean", bins=theta_bin_edges)
 epsilon_sigma, bin_edges, binnumber = binned_statistic(theta, epsilon, statistic=np.std, bins=theta_bin_edges)
+N_in_bin, bin_edges = np.histogram(theta, bin_edges)
 theta_bin_centers = theta_bin_edges[:-1] + (theta_bin_edges[1] - theta_bin_edges[0])/2
-np.savetxt("data.csv", np.stack([theta_bin_centers, epsilon_mean, epsilon_sigma], 1), delimiter=", ")
+np.savetxt("data.csv", np.stack([theta_bin_centers, epsilon_mean, epsilon_sigma/np.sqrt(N_in_bin)], 1), delimiter=", ")
 
 
 ### FITTING ###

### 2018-04-29 paper.tex
Added references bibtex file

@@
-\documentclass[]{article}
+\documentclass[10pt]{article}
 \usepackage[margin=1in]{geometry}
 \usepackage{parskip}
+\usepackage{microtype}
+\usepackage{natbib}
+\usepackage{graphicx}
 % \usepackage{txfonts}
 
+\graphicspath{ {figures/} }
+
 \begin{document}
+
 \title{Distinguishing NFW and Isothermal Density Profiles with Weak Gravitational Lensing}
-\author{}
+\author{Ian Holst and Doyee Byun}
 \date{\today}
@@
 \section{Introduction}
+Background/history of this research topic, goals for this section
 
 \subsection{General spherical density profile $\rho(r)$}
-Using thin lens approximation
+Here we define our conventions for various lensing quantities, which mainly conform to those used by \citet{Dodelson2017}. We use the thin lens approximation and assume spherical lens profiles.
 
 Projected surface density at radius R
-\[\Sigma(R) = \int_{-\infty}^{\infty}{\rho(\sqrt{R^2 + z^2}) dz}\]
+\[\Sigma(R) = \int_{-\infty}^{\infty}{dz\ \rho(\sqrt{R^2 + z^2})}\]
 
@@
 \[\epsilon_i = \frac{2 \gamma_i/(1 - \kappa)}{1 + \gamma^2/(1 - \kappa)^2}\]
+\[\epsilon =  -\epsilon_1 \cos{2\phi} -\epsilon_2 \sin{2\phi}\]
 
@@
 
-\[\rho_\mathrm{NFW}(r) = \frac{\rho_\mathrm{crit} \delta_C}{(r/r_s)\left(1 + r/r_s\right)^2}\]
+\[\rho_\mathrm{NFW}(r) = \frac{\rho_\mathrm{crit} \delta_c}{(r/r_s)\left(1 + r/r_s\right)^2}\]
 
-\[\Sigma_\mathrm{NFW}(R) = \frac{2 \rho_\mathrm{crit} \delta_C r_s}{(R/r_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(R/r_s)^2 - 1}}  \arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) \right)\]
+\[\Sigma_\mathrm{NFW}(R) = \frac{2 \rho_\mathrm{crit} \delta_c r_s}{(R/r_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(R/r_s)^2 - 1}}  \arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) \right)\]
 [Bartelmann 2001]
 
-\[\overline{\Sigma}_\mathrm{NFW}(R) = \frac{4 \rho_\mathrm{crit} \delta_C r_s}{(R/r_s)^2} \left(
+\[\overline{\Sigma}_\mathrm{NFW}(R) = \frac{4 \rho_\mathrm{crit} \delta_c r_s}{(R/r_s)^2} \left(
     \frac{2}{\sqrt{(R/r_s)^2 - 1}} ~\arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) + \ln{\left(\frac{R/r_s}{2}\right)}
@@
 
-\[\Sigma_\mathrm{NFW}(\theta) = \frac{2 \rho_\mathrm{crit} \delta_C D_L \theta_s}{(\theta/\theta_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(\theta/\theta_s)^2 - 1}} \arctan\left(\sqrt{\frac{\theta/\theta_s - 1}{\theta/\theta_s + 1}} \right) \right)\]
+\[\Sigma_\mathrm{NFW}(\theta) = \frac{2 \rho_\mathrm{crit} \delta_c D_L \theta_s}{(\theta/\theta_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(\theta/\theta_s)^2 - 1}} \arctan\left(\sqrt{\frac{\theta/\theta_s - 1}{\theta/\theta_s + 1}} \right) \right)\]
 
-\[\overline{\Sigma}_\mathrm{NFW}(\theta) = \frac{4 \rho_\mathrm{crit} \delta_C D_L \theta_s}{(\theta/\theta_s)^2} \left(
+\[\overline{\Sigma}_\mathrm{NFW}(\theta) = \frac{4 \rho_\mathrm{crit} \delta_c D_L \theta_s}{(\theta/\theta_s)^2} \left(
     \frac{2}{\sqrt{(\theta/\theta_s)^2 - 1}} ~\arctan\left(\sqrt{\frac{\theta/\theta_s - 1}{\theta/\theta_s + 1}} \right) + \ln{\left(\frac{\theta/\theta_s}{2}\right)}
@@
 
-We switch the dependence to $M_{200}$ and $C$ with:
+We switch the dependence to $M_{200}$ and $c$ with:
 
-\[\delta_C = \frac{200}{3} \frac{C^3}{\ln(1 + C) - C/(1 + C)}\]
-\[r_s = \frac{r_{200}}{C}\]
+\[\delta_c = \frac{200}{3} \frac{c^3}{\ln(1 + c) - c/(1 + c)}\]
+\[r_s = \frac{r_{200}}{c}\]
 \[r_{200} = \left( \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}} \right)^{1/3}\]
-\[C = \frac{r_{200}}{r_s}\]
+\[c = \frac{r_{200}}{r_s}\]
 
@@
 
+\bibliographystyle{plainnat}
+\bibliography{references}
+
 \end{document}

### 2018-05-02 paper.tex
Updates to paper

@@
 
-\[\Sigma_\mathrm{iso}(R) = \frac{\sigma^2}{2 G \sqrt{R^2 + {r_c}^2}}\]
-
-\[\overline{\Sigma}_\mathrm{iso}(R) = \frac{\sigma^2 \left(\sqrt{R^2 + {r_c}^2} - r_c \right)}{G R^2}\]
-
-In terms of angles:
+% \[\Sigma_\mathrm{iso}(R) = \frac{\sigma^2}{2 G \sqrt{R^2 + {r_c}^2}}\]
+%
+% \[\overline{\Sigma}_\mathrm{iso}(R) = \frac{\sigma^2 \left(\sqrt{R^2 + {r_c}^2} - r_c \right)}{G R^2}\]
+% 
+% In terms of angles:
 
@@
 
-\[\Sigma_\mathrm{NFW}(R) = \frac{2 \rho_\mathrm{crit} \delta_c r_s}{(R/r_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(R/r_s)^2 - 1}}  \arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) \right)\]
-[Bartelmann 2001]
-
-\[\overline{\Sigma}_\mathrm{NFW}(R) = \frac{4 \rho_\mathrm{crit} \delta_c r_s}{(R/r_s)^2} \left(
-    \frac{2}{\sqrt{(R/r_s)^2 - 1}} ~\arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) + \ln{\left(\frac{R/r_s}{2}\right)}
-\right)\]
-
-In terms of angles:
+% \[\Sigma_\mathrm{NFW}(R) = \frac{2 \rho_\mathrm{crit} \delta_c r_s}{(R/r_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(R/r_s)^2 - 1}}  \arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) \right)\]
+%
+%
+% \[\overline{\Sigma}_\mathrm{NFW}(R) = \frac{4 \rho_\mathrm{crit} \delta_c r_s}{(R/r_s)^2} \left(
+%     \frac{2}{\sqrt{(R/r_s)^2 - 1}} ~\arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) + \ln{\left(\frac{R/r_s}{2}\right)}
+% \right)\]
+%
+% In terms of angles:
 
@@
 \right)\]
+
+Similar convention used by \citet{Bartelmann2001}
 
@@
 
+Estimating ellipticity has well-documented issues [cite] due to noise and PSF
+
+\newpage
+
 \section{Methods}
 
-\subsection{Current plan}
+\begin{enumerate}
+    \item Calculate tangential shear and deflection angle for NFW and cored isothermal profiles.
+    \item Consider single foreground lens halo with many background galaxies.
     \begin{itemize}
-    \item Calculate tangential shear and deflection angle for NFW and SIS
-    \item Consider single foreground lens halo with many background galaxies
-    \item How to arrange and distribute background halos?
+        \item Start with one NFW halo, then maybe consider more tests.
+    \end{itemize}
+    \item Construct background galaxies:
     \begin{itemize}
-        \item Initial ellipticity
-        \item angular density on sky
-        \item sizes
+        \item Number density on sky: 50 galaxies/square arcminute
+        \item Intrinsic ellipticity drawn from Gaussian distribution with $\mu=0, \sigma=0.2$
+        \item Assume they are all that the same distance $D_S$ since this can be determined by redshift (neglecting some noise)
     \end{itemize}
-    \item Apply shear and deflection angle to background galaxies
-    \item Attempt to fit both profiles, subtracting intrinsic shear, see if the fit is distinguishable
-    \item How many foreground halos to test? - start with 1
-    \item What redshift is $\rho_\mathrm{crit}$ evaluated at? - at halo redshift
+    \item Recommended values:
+    \begin{itemize}
+        \item $z_L = 0.3$
+        \item $z_S = 1.0$
+        \item $M_{halo} = 10^{15} M_\odot$
+    \end{itemize}
+    \item Apply shear and deflection angle to background galaxies, get fake data: $N$ sets of $\epsilon_1$, $\epsilon_2$, $\theta_1$, $\theta_2$
+    \item Bin galaxies in annuli by $\theta$ value (use log bins for theta)
+    \item Calculate mean and standard deviation of ellipticity
+    \item Attempt to fit both NFW and isothermal profiles, see if the fit is distinguishable
+\end{enumerate}
 
+\subsection{Questions}
+\begin{itemize}
+    \item How to properly do sigma contours?
+    \item What theta range should we look at? (5 arcminutes?)
+    \item What redshift is $\rho_\mathrm{crit}$ evaluated at? - at halo redshift - can we use current time?
+    \item Using $c = 10$?
+    \item Where to go from here?
 \end{itemize}
 
-Fake data:
-N sets of e1, e2, theta1, theta2
-
-Analyzing data:
-make histogram in annulus
-mean and standard deviation
-use log bins for theta
-
-50 gals/square arcminute
-5 arcminutes
-$z_L = 0.3$
-$z_S = 1$
-$M_{halo} = 10^15$ solar masses
-instrinsic ellipticity from gaussian with width 0.2
-
-Assume same DS since this can be determined by redshift anyway
-
-estimating ellipticity has well-documented issues [cite] due to noise and PSF
+\section{Results}
 

### 2018-05-05 paper.tex
New subsection in introduction to describe project purpose.

@@
 \section{Introduction}
-Background/history of this research topic, goals for this section
+Two commonly used density profiles in weak gravitational lensing are the isothermal profile and the Navarro-Frenk-White (NFW) profile.
 
@@
 
+\subsection{Project Purpose}
+The goal of this project is to devise a method to analyze lensed galaxy cluster data and find which density profile is more probable between the isothermal and NFW profiles.
+
 \newpage

### 2018-05-05 paper.tex
building up methods section. nothing much just barebones for now
More elaboration in the abstract, as well as the beginning of the intro

@@
 We examine the feasibility of distinguishing NFW and cored isothermal density profiles using weak gravitational lensing shear.
+ To do so, we use Python to model lenses in the two different profiles, as well as background galaxies to be lensed.
+ Analyzing the data of these lensed galaxies gives us insight into how we can distinguish the differences between the two profiles.
 \end{abstract}
@@
 Two commonly used density profiles in weak gravitational lensing are the isothermal profile and the Navarro-Frenk-White (NFW) profile.
+We start with introducing the general characteristics of spherical density profiles, followed by cored isothermal and NFW profiles.
+We then describe the purpose of our project, to distinguish between NFW and isothermal profiles, in detail.
 
 \subsection{General spherical density profile $\rho(r)$}
+We describe the common characteristics of spherical density profiles.
 Here we define our conventions for various lensing quantities, which mainly conform to those used by \citet{Dodelson2017}. We use the thin lens approximation and assume spherical lens profiles.
 
-Projected surface density at radius R
+The projected surface density at radius R is defined by
 \[\Sigma(R) = \int_{-\infty}^{\infty}{dz\ \rho(\sqrt{R^2 + z^2})}\]
 
-Average projected surface density within radius R
+while the average projected surface density within R is
 \[\overline{\Sigma}(R) = \frac{1}{\pi R^2} \int_0^{2\pi}{d\phi \int_0^{R}{dR'~\Sigma(R')R'}}\]
 
-Critical surface density
+The critical surface density is
 \[\Sigma_\mathrm{crit} = \frac{c^2}{4\pi G} \frac{D_S}{D_{SL} D_L}\]
@@
 \section{Methods}
+\subsection{Calculation of Shear and Deflection Angles for Each Profile}
+
+\subsection{Modelling of Foreground Lens and Background Galaxies}
 

### 2018-05-06 paper.tex
Categorized content to be placed in methods section into subsections
more flesh to paper

@@
 
-In small angle approximation, any length $R = D_L \theta$.
+At small angles, we can assume from small angle approximations that $R = D_L \theta$.
 
@@
 \subsection{Cored Isothermal Sphere Profile}
+
+The isothermal sphere profile is commonly used thanks to the convenience in simplifications.
 
@@
 \subsection{Modelling of Foreground Lens and Background Galaxies}
-
 \begin{enumerate}
-    \item Calculate tangential shear and deflection angle for NFW and cored isothermal profiles.
     \item Consider single foreground lens halo with many background galaxies.
@@
     \end{itemize}
-    \item Apply shear and deflection angle to background galaxies, get fake data: $N$ sets of $\epsilon_1$, $\epsilon_2$, $\theta_1$, $\theta_2$
+\end{enumerate}
+
+\subsection{Generating Simulated Data}
+\begin{enumerate}
+\item Apply shear and deflection angle to background galaxies, get simulated data: $N$ sets of $\epsilon_1$, $\epsilon_2$, $\theta_1$, $\theta_2$
+\end{enumerate}
+
+\subsection{Data Analysis and Density Profile Determination}
+\begin{enumerate}
 \item Bin galaxies in annuli by $\theta$ value (use log bins for theta)
@@
 
-\section{Results}
+\section{Results and Conclusion}
+
+From our data analysis, we were able to find the more probable density profile of a simulated data set.
+Future goals include the use of these methods to analyze observed data of galaxy clusters to find the density profile of their lenses.
 

### 2018-05-06 analysis.py
Bayesian probability pretty much completed

@@ -45,7 +45,7 @@ theta = np.sqrt(theta_x**2 + theta_y**2)
 epsilon = -e1*np.cos(2*phi) - e2*np.sin(2*phi)
 
 # Bin into annuli and calculate mean and standard deviation
-theta_bin_edges = np.linspace(100*u.arcsec, viewSize/np.sqrt(2), 40)
+theta_bin_edges = np.linspace(10*u.arcsec, viewSize/np.sqrt(2), 40)
 epsilon_mean, bin_edges, binnumber = binned_statistic(theta, epsilon, statistic="mean", bins=theta_bin_edges)
 epsilon_sigma, bin_edges, binnumber = binned_statistic(theta, epsilon, statistic=np.std, bins=theta_bin_edges)
 N_in_bin, bin_edges = np.histogram(theta, bin_edges)
@@ -54,26 +54,27 @@ np.savetxt("data.csv", np.stack([theta_bin_centers, epsilon_mean, epsilon_sigma/
 
 
 ### FITTING ###
+# python hates fitting
 
-def nfw_ellipticity(theta, M200, C):
-    halo = NFWHalo(M200*u.solMass, C, DL)
-    return np.array([halo.ellipticity(t*u.arcsec, DS) for t in theta])
-
-def iso_ellipticity(theta, M200, rc):
-    halo = IsothermalHalo(M200*u.solMass, rc*u.kpc, DL)
-    return np.array([halo.ellipticity(t*u.arcsec, DS) for t in theta])
-
-BOUNDS = [[0,0], [np.inf, np.inf]]
-optimalNFWParams, covariance = curve_fit(nfw_ellipticity, theta_bin_centers, epsilon_mean, p0=[1e16, 20], bounds=BOUNDS, sigma=epsilon_sigma)
-optimalIsoParams, covariance = curve_fit(iso_ellipticity, theta_bin_centers, epsilon_mean, p0=[1e16, 20], bounds=BOUNDS, sigma=epsilon_sigma)
-
-plt.figure()
-plt.plot(theta_bin_centers, nfw_ellipticity(theta_bin_centers, 1e15, 10))
-plt.plot(theta_bin_centers, epsilon_mean)
-plt.plot(theta_bin_centers, nfw_ellipticity(theta_bin_centers, *optimalNFWParams))
-plt.plot(theta_bin_centers, iso_ellipticity(theta_bin_centers, *optimalIsoParams))
[…]

### 2018-05-06 lensing.py

@@ -25,7 +25,7 @@ def SIGMA_CRIT(DS, DL):
     DSL = DS - DL
     return c**2 / (4 * np.pi * G) * (DS / (DSL * DL))
 
-def lensingImage(halo, backgroundGalaxies, v, a):
+def lensingImage(halo, backgroundGalaxies, v, a=1):
     # Produce a mock lensing image with a halo and a population of background galaxies
     # v is the view width and a is the size of galaxies
     fig = plt.figure()

### 2018-05-06 analysis.py
Added accurate angular diameter distances and figures.py

@@ -10,18 +10,22 @@ from lensing import *
 galaxyNumberDensity = 50/u.arcmin**2
 viewSize = 1000*u.arcsec
 Ngal = round((viewSize**2 * galaxyNumberDensity).to_value(""))
+zS = 1.0
+zL = 0.3
+DS = cosmology.Planck15.comoving_distance(zS) / (1 + zS)
+DL = cosmology.Planck15.comoving_distance(zL) / (1 + zL)
 
 lensHalo = NFWHalo(
     M200=1e15*u.solMass,
     C=10,
-    DL=1*u.Gpc)
+    DL=DL)
 
 backgroundGalaxies = [BackgroundGalaxy(
     Bx=(viewSize*np.random.rand() - viewSize/2),
     By=(viewSize*np.random.rand() - viewSize/2),
     e1=np.random.normal(0, 0.2),
     e2=np.random.normal(0, 0.2),
-    DS=3*u.Gpc) for i in range(Ngal)]
+    DS=DS) for i in range(Ngal)]
 
 lensedBackgroundGalaxies = [lensHalo.lense(gal) for gal in backgroundGalaxies]
 
@@ -35,21 +39,25 @@ phi = np.array([lgal.phi.to_value(u.rad) for lgal in lensedBackgroundGalaxies])
 ### ANALYSIS ###
 
 # Assume we have a dataset of N galaxies with positions (theta_x, theta_y) and ellipticities (e1, e2)
-# Assumer they all have same DS and DL is known
-DS = 3*u.Gpc
-DL = 1*u.Gpc
+# Assume they all have same known DS and DL
 # Assume these are numpy arrays of length N
 
 # Calculate radial position theta and magnitude of ellipticity epsilon
 theta = np.sqrt(theta_x**2 + theta_y**2)
 epsilon = -e1*np.cos(2*phi) - e2*np.sin(2*phi)
-
+# Create theta bins
+bin_start = 10*u.arcsec
+bin_stop = viewSize/np.sqrt(2)
+N_bins = 40
+theta_bin_edges = np.linspace(bin_start, bin_stop, N_bins)
 # Bin into annuli and calculate mean and standard deviation
-theta_bin_edges = np.linspace(10*u.arcsec, viewSize/np.sqrt(2), 40)
 epsilon_mean, bin_edges, binnumber = binned_statistic(theta, epsilon, statistic="mean", bins=theta_bin_edges)
[…]

### 2018-05-06 figures.py

@@ -1,0 +1,45 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import astropy.cosmology as cosmology
+import astropy.units as u
+from scipy.optimize import curve_fit
+from scipy.stats import binned_statistic
+from lensing import *
+
+# here is an example of lensing very close to the halo
+galaxyNumberDensity = 50/u.arcmin**2
+viewSize = 1000*u.arcsec
+Ngal = round((viewSize**2 * galaxyNumberDensity).to_value(""))
+zS = 1.0
+zL = 0.3
+DS = cosmology.Planck15.comoving_distance(zS) / (1 + zS)
+DL = cosmology.Planck15.comoving_distance(zL) / (1 + zL)
+
+v = 100 # view radius
+
+halo_iso = IsothermalHalo(
+    M200=1e15*u.solMass,
+    rc=10*u.kpc,
+    DL=1*u.Gpc)
+
+halo_nfw = NFWHalo(
+    M200=1e15*u.solMass,
+    C=10,
+    DL=1*u.Gpc)
+
+halo_iso.plotProperties(0.0001, v, 500, 3*u.Gpc)
+print("theta_c:", halo_iso.Tc.to(u.arcsec))
+print("theta_0:", halo_iso.T0(3*u.Gpc).to(u.arcsec))
+
+halo_nfw.plotProperties(0.0001, v, 500, 3*u.Gpc)
+print("theta_s:", halo_nfw.Ts.to(u.arcsec))
+
+backgroundGalaxies = [BackgroundGalaxy(
+    Bx=(v*np.random.rand()-v/2)*u.arcsec,
+    By=(v*np.random.rand()-v/2)*u.arcsec,
+    e1=0,
+    e2=0,
+    DS=3*u.Gpc) for i in range(1000)]
+
+lensingImage(halo_iso, backgroundGalaxies, v)
+lensingImage(halo_nfw, backgroundGalaxies, v)

### 2018-05-06 lensing.py

@@ -13,7 +13,7 @@ plt.rcParams["figure.dpi"] = 100
 ### CONSTANTS ###
 c = const.c
 G = const.G
-H0 = cosmology.default_cosmology.get().H(0)
+H0 = cosmology.Planck15.H0
 RHO_CRIT = 3 * H0**2 / (8 * np.pi * G) # only use rho_crit at current time
 u.set_enabled_equivalencies(u.dimensionless_angles()) # allow angles to be dimensionless
 
@@ -163,36 +163,3 @@ class LensedBackgroundGalaxy:
                        width=a,
                        height=a*(e+1)/(e-1),
                        angle=self.phi.to_value(u.degree))
-
-
-
-if __name__ == '__main__':
-    # here is an example of lensing very close to the halo
-    v = 100 # view radius
-
-    halo_iso = IsothermalHalo(
-        M200=1e15*u.solMass,
-        rc=10*u.kpc,
-        DL=1*u.Gpc)
-
-    halo_nfw = NFWHalo(
-        M200=1e15*u.solMass,
-        C=10,
-        DL=1*u.Gpc)
-
-    halo_iso.plotProperties(0.0001, v, 500, 3*u.Gpc)
-    print("theta_c:", halo_iso.Tc.to(u.arcsec))
-    print("theta_0:", halo_iso.T0(3*u.Gpc).to(u.arcsec))
-
-    halo_nfw.plotProperties(0.0001, v, 500, 3*u.Gpc)
-    print("theta_s:", halo_nfw.Ts.to(u.arcsec))
-
-    backgroundGalaxies = [BackgroundGalaxy(
-        Bx=(v*np.random.rand()-v/2)*u.arcsec,
-        By=(v*np.random.rand()-v/2)*u.arcsec,
-        e1=0,
-        e2=0,
-        DS=3*u.Gpc) for i in range(1000)]
-
-    lensingImage(halo_iso, backgroundGalaxies, v)
-    lensingImage(halo_nfw, backgroundGalaxies, v)

### 2018-05-07 analysis.py
Working on figures

@@ -5,6 +5,7 @@ import astropy.units as u
 from scipy.optimize import curve_fit
 from scipy.stats import binned_statistic
 from lensing import *
+np.random.seed(0)
 
 ### DATA GENERATION ###
 galaxyNumberDensity = 50/u.arcmin**2

### 2018-05-07 figures.py

@@ -5,41 +5,80 @@ import astropy.units as u
 from scipy.optimize import curve_fit
 from scipy.stats import binned_statistic
 from lensing import *
+np.random.seed(0)
+plt.rcParams["font.family"] = "serif"
+plt.rcParams["mathtext.fontset"] = "cm"
+plt.rcParams["text.usetex"] = True
+plt.rcParams["figure.dpi"] = 150
+
 
 # here is an example of lensing very close to the halo
-galaxyNumberDensity = 50/u.arcmin**2
-viewSize = 1000*u.arcsec
+galaxyNumberDensity = 1000/(100*u.arcsec)**2
+viewSize = 100*u.arcsec
 Ngal = round((viewSize**2 * galaxyNumberDensity).to_value(""))
 zS = 1.0
 zL = 0.3
 DS = cosmology.Planck15.comoving_distance(zS) / (1 + zS)
 DL = cosmology.Planck15.comoving_distance(zL) / (1 + zL)
 
-v = 100 # view radius
-
 halo_iso = IsothermalHalo(
     M200=1e15*u.solMass,
     rc=10*u.kpc,
-    DL=1*u.Gpc)
+    DL=DL)
 
 halo_nfw = NFWHalo(
     M200=1e15*u.solMass,
     C=10,
-    DL=1*u.Gpc)
+    DL=DL)
 
-halo_iso.plotProperties(0.0001, v, 500, 3*u.Gpc)
+def plotProperties(halo, start, stop, step, DS, name):
+    # Plot the shear, ellipticity, convergence, and magnification for the halo
+    theta = np.linspace(start, stop, step)
+    epsilon = np.array([halo.ellipticity(t, DS) for t in theta])
+    gamma = np.array([halo.shear(t, DS) for t in theta])
+    kappa = np.array([(halo.surfaceDensity(t) / SIGMA_CRIT(DS, halo.DL)).to_value("") for t in theta])
+    mu = 1/((1-kappa)**2 - gamma**2)
+    plt.figure()
+    plt.plot(theta, epsilon)
+    plt.plot(theta, gamma)
+    plt.plot(theta, kappa)
+    # plt.plot(theta, mu)
+    plt.legend(["$\epsilon$", "$\gamma$", "$\kappa$", "$\mu$"])
+    plt.xlabel("$\\theta$ ($^{\prime\prime}$)")
+    plt.ylim(-1,3)
[…]

### 2018-05-07 lensing.py

@@ -25,20 +25,6 @@ def SIGMA_CRIT(DS, DL):
     DSL = DS - DL
     return c**2 / (4 * np.pi * G) * (DS / (DSL * DL))
 
-def lensingImage(halo, backgroundGalaxies, v, a=1):
-    # Produce a mock lensing image with a halo and a population of background galaxies
-    # v is the view width and a is the size of galaxies
-    fig = plt.figure()
-    ax = fig.add_subplot(111, aspect="equal")
-    ax.set_xlim(-v/2,v/2)
-    ax.set_ylim(-v/2,v/2)
-    for gal in backgroundGalaxies:
-        lensedGal = halo.lense(gal)
-        lensedGalEllipse = lensedGal.ellipse(a)
-        lensedGalEllipse.set_facecolor(np.random.rand(3))
-        ax.add_artist(lensedGalEllipse)
-    return plt.show()
-
 
 ### GALAXY/HALO OBJECTS ###
 
@@ -71,24 +57,6 @@ class Halo:
         e1 = galaxy.e1 - e*np.cos(2*phi) # TODO: how do ellipticities add?
         e2 = galaxy.e2 - e*np.sin(2*phi)
         return LensedBackgroundGalaxy(Tx, Ty, e1, e2, galaxy.DS)
-
-    def plotProperties(self, start, stop, step, DS):
-        # Plot the shear, ellipticity, convergence, and magnification for the halo
-        theta = np.linspace(start, stop, step)*u.arcsec
-        epsilon = np.array([self.ellipticity(t, DS) for t in theta])
-        gamma = np.array([self.shear(t, DS) for t in theta])
-        kappa = np.array([(self.surfaceDensity(t) / SIGMA_CRIT(DS, self.DL)).to_value("") for t in theta])
-        mu = 1/((1-kappa)**2 - gamma**2)
-        plt.figure()
-        plt.plot(theta, epsilon)
-        plt.plot(theta, gamma)
-        plt.plot(theta, kappa)
-        plt.plot(theta, mu)
-        plt.legend(["$\epsilon$", "$\gamma$", "$\kappa$", "$\mu$"])
-        plt.xlabel("$\\theta$ (arcseconds)")
-        plt.ylim(-10,10)
-        return plt.show()
-
 
 
 class NFWHalo(Halo):
@@ -124,7 +92,7 @@ class IsothermalHalo(Halo):
[…]

### 2018-05-07 paper.tex
updated conclusion
Paper updates

@@
  To do so, we use Python to model lenses in the two different profiles, as well as background galaxies to be lensed.
- Analyzing the data of these lensed galaxies gives us insight into how we can distinguish the differences between the two profiles.
+ Analyzing the simulated data of these lensed galaxies gives us insight into how we can distinguish the differences between the two profiles.
+ This method is expected to be helpful in the analysis of real observation data in the future.
 \end{abstract}
@@
 \section{Introduction}
+Gravitational lensing allows us to investigate the matter density distributions of cosmic objects by observing the characteristic distortions imparted on other objects in the background.
+The principle is applicable on a large range of scales, from all-sky mass maps based on cosmic microwave background shear to studies of individual galaxies and clusters.
+A common use of lensing is
+
 Two commonly used density profiles in weak gravitational lensing are the isothermal profile and the Navarro-Frenk-White (NFW) profile.
@@
 
-\subsection{General spherical density profile $\rho(r)$}
 We describe the common characteristics of spherical density profiles.
 Here we define our conventions for various lensing quantities, which mainly conform to those used by \citet{Dodelson2017}. We use the thin lens approximation and assume spherical lens profiles.
+Consider such a spherically symmetric halo density profile $\rho(r)$
 
-The projected surface density at radius R is defined by
-\[\Sigma(R) = \int_{-\infty}^{\infty}{dz\ \rho(\sqrt{R^2 + z^2})}\]
+The projected surface density at radius R on the projected plane is defined, considering the z axis to be along the line of sight:
+\begin{equation}
+\Sigma(R) = \int_{-\infty}^{\infty}{dz\ \rho(\sqrt{R^2 + z^2})}
+\end{equation}
 
-while the average projected surface density within R is
-\[\overline{\Sigma}(R) = \frac{1}{\pi R^2} \int_0^{2\pi}{d\phi \int_0^{R}{dR'~\Sigma(R')R'}}\]
+An important related measure in gravitational lensing is the average projected surface density within radius R:
+\begin{equation}
+\overline{\Sigma}(R) = \frac{1}{\pi R^2} \int_0^{2\pi}{d\phi \int_0^{R}{dR'~\Sigma(R')R'}}
+\end{equation}
 
-The critical surface density is
-\[\Sigma_\mathrm{crit} = \frac{c^2}{4\pi G} \frac{D_S}{D_{SL} D_L}\]
+The critical surface density marks the typical boundary between what is considered strong and weak lensing:
+\begin{equation}
+\Sigma_\mathrm{crit} = \frac{c^2}{4\pi G} \frac{D_S}{D_{SL} D_L}
+\end{equation}
 
-Convergence
-\[\kappa(\theta) = \frac{\Sigma(\theta)}{\Sigma_\mathrm{crit}}\]
+We also define the convergence, $\kappa$ to be
+\begin{equation}
+\kappa(\theta) = \frac{\Sigma(\theta)}{\Sigma_\mathrm{crit}}
+\end{equation}
 
-Tangential shear
-\[\gamma_t(\theta) = \overline{\kappa}(\theta) - \kappa(\theta)\]
-\[\gamma_1 = -\gamma_t \cos{2\phi}\]
-\[\gamma_2 = -\gamma_t \sin{2\phi}\]
-\[\gamma = \gamma_t = \sqrt{{\gamma_1}^2 + {\gamma_2}^2} = -\gamma_1 \cos{2\phi} -\gamma_2 \sin{2\phi}\]
+Tangential shear, along with the components of shear are shown as follows.
+\begin{equation}
+\gamma_t(\theta) = \overline{\kappa}(\theta) - \kappa(\theta)
+\end{equation}
 
-Deflection angle
-\[\vec{\alpha}(\vec{\theta}) = \overline{\kappa}(\theta)\vec{\theta}\]
-\[\vec{\beta} = \vec{\theta} - \vec{\alpha} = (1 - \overline{\kappa}(\theta))\vec{\theta} \]
+\begin{equation}
+\gamma_1 = -\gamma_t \cos{2\phi}
+\gamma_2 = -\gamma_t \sin{2\phi}
+\end{equation}
 
-Ellipticity
-\[\epsilon_i = \frac{2 \gamma_i/(1 - \kappa)}{1 + \gamma^2/(1 - \kappa)^2}\]
-\[\epsilon =  -\epsilon_1 \cos{2\phi} -\epsilon_2 \sin{2\phi}\]
+It can be shown that for a spherical lens profile, the only component of shear should be the tangential shear, $\gamma_t$:
+\citep{Dodelson2017}
+\begin{equation}
+\gamma = \gamma_t = \sqrt{{\gamma_1}^2 + {\gamma_2}^2} = -\gamma_1 \cos{2\phi} -\gamma_2 \sin{2\phi}
+\end{equation}
+
+Deflection angle is
+\begin{equation}
+\vec{\alpha}(\vec{\theta}) = \overline{\kappa}(\theta)\vec{\theta}
+\end{equation}
+\begin{equation}
+\vec{\beta} = \vec{\theta} - \vec{\alpha} = (1 - \overline{\kappa}(\theta))\vec{\theta}
+\end{equation}
+
+while ellipticity is
+\begin{equation}
+\epsilon_i = \frac{2 \gamma_i/(1 - \kappa)}{1 + \gamma^2/(1 - \kappa)^2}
+\end{equation}
+\begin{equation}
+\epsilon =  -\epsilon_1 \cos{2\phi} -\epsilon_2 \sin{2\phi}
+\end{equation}
 
@@
 
-\subsection{Cored Isothermal Sphere Profile}
+\section{Cored Isothermal Sphere Profile}
+The cored isothermal sphere (CIS) profile is related to the singular isothermal sphere, which is often used to describe halos and other collapsed astrophysical objects because of its simple formulation.
+Unlike the singular isothermal sphere, the cored isothermal sphere does not have a density singularity at its center due to a finite core radius $r_c$.
+The CIS density profile is defined:
 
-The isothermal sphere profile is commonly used thanks to the convenience in simplifications.
+\begin{equation}
+\rho_\mathrm{iso}(r) = \frac{\sigma^2}{2\pi G (r^2 + {r_c}^2)}
+\end{equation}
 
-\[\rho_\mathrm{iso}(r) = \frac{\sigma^2}{2\pi G (r^2 + {r_c}^2)}\]
-
-% \[\Sigma_\mathrm{iso}(R) = \frac{\sigma^2}{2 G \sqrt{R^2 + {r_c}^2}}\]
+where $\sigma^2$ is the velocity dispersion.
+https://arxiv.org/pdf/astro-ph/9810164.pdf
+% \begin{equation}\Sigma_\mathrm{iso}(R) = \frac{\sigma^2}{2 G \sqrt{R^2 + {r_c}^2}}
+% \end{equation}
 %
-% \[\overline{\Sigma}_\mathrm{iso}(R) = \frac{\sigma^2 \left(\sqrt{R^2 + {r_c}^2} - r_c \right)}{G R^2}\]
+% \begin{equation}\overline{\Sigma}_\mathrm{iso}(R) = \frac{\sigma^2 \left(\sqrt{R^2 + {r_c}^2} - r_c \right)}{G R^2}
+% \end{equation}
 %
@@
 
-\[\Sigma_\mathrm{iso}(\theta) = \frac{\sigma^2}{2 G D_L \sqrt{\theta^2 + {\theta_c}^2}}\]
+\begin{equation}
+\Sigma_\mathrm{iso}(\theta) = \frac{\sigma^2}{2 G D_L \sqrt{\theta^2 + {\theta_c}^2}}
+\end{equation}
 
-\[\overline{\Sigma}_\mathrm{iso}(\theta) = \frac{\sigma^2 \left(\sqrt{\theta^2 + {\theta_c}^2} - \theta_c \right)}{G D_L \theta^2}\]
+\begin{equation}
+\overline{\Sigma}_\mathrm{iso}(\theta) = \frac{\sigma^2 \left(\sqrt{\theta^2 + {\theta_c}^2} - \theta_c \right)}{G D_L \theta^2}
+\end{equation}
 
-\[\gamma_\mathrm{iso}(\theta) = \frac{\sigma^2 \left(\sqrt{\theta^2 + {\theta_c}^2} - \theta_c \right)}{\Sigma_\mathrm{crit} G D_L \theta^2} - \frac{\sigma^2}{2 \Sigma_\mathrm{crit} G D_L \sqrt{\theta^2 + {\theta_c}^2}}\]
+\begin{equation}
+\gamma_\mathrm{iso}(\theta) = \frac{\sigma^2 \left(\sqrt{\theta^2 + {\theta_c}^2} - \theta_c \right)}{\Sigma_\mathrm{crit} G D_L \theta^2} - \frac{\sigma^2}{2 \Sigma_\mathrm{crit} G D_L \sqrt{\theta^2 + {\theta_c}^2}}
+\end{equation}
 
@@
 
-\[\sigma^2 = \frac{M_{200} G}{2 \left( r_{200} - r_c \arctan{\left(\frac{r_{200}}{r_c}\right)} \right)}\]
+\begin{equation}
+\sigma^2 = \frac{M_{200} G}{2 \left( r_{200} - r_c \arctan{\left(\frac{r_{200}}{r_c}\right)} \right)}
+\end{equation}
 
@@
 
-\[M_{200} = 200 \rho_\mathrm{crit} \frac{4}{3} \pi {r_{200}}^3\]
-\[M_{200} = M_\mathrm{enc}(r_{200}) = \frac{2 \sigma^2}{G} \left( r_{200} - r_c \arctan{\left(\frac{r_{200}}{r_c}\right)} \right)\]
-\[r_{200} = \left( \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}} \right)^{1/3}\]
+\begin{equation}
+M_{200} = 200 \rho_\mathrm{crit} \frac{4}{3} \pi {r_{200}}^3
+\end{equation}
+\begin{equation}
+M_{200} = M_\mathrm{enc}(r_{200}) = \frac{2 \sigma^2}{G} \left( r_{200} - r_c \arctan{\left(\frac{r_{200}}{r_c}\right)} \right)
+\end{equation}
+\begin{equation}
+r_{200} = \left( \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}} \right)^{1/3}
+\end{equation}
 
-Ellipticity equations are very ugly but trivial to calculate from the shear.
+The ellipticity equations, while not quite elegant, are trivial to calculate from the shear.
 
-\subsection{Navarro-Frenk-White (NFW) Profile}
+\section{Navarro-Frenk-White (NFW) Profile}
 
-\[\rho_\mathrm{NFW}(r) = \frac{\rho_\mathrm{crit} \delta_c}{(r/r_s)\left(1 + r/r_s\right)^2}\]
+\begin{equation}
+\rho_\mathrm{NFW}(r) = \frac{\rho_\mathrm{crit} \delta_c}{(r/r_s)\left(1 + r/r_s\right)^2}
+\end{equation}
 
-% \[\Sigma_\mathrm{NFW}(R) = \frac{2 \rho_\mathrm{crit} \delta_c r_s}{(R/r_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(R/r_s)^2 - 1}}  \arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) \right)\]
+% \begin{equation}\Sigma_\mathrm{NFW}(R) = \frac{2 \rho_\mathrm{crit} \delta_c r_s}{(R/r_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(R/r_s)^2 - 1}}  \arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) \right)
+% \end{equation}
 %
 %
-% \[\overline{\Sigma}_\mathrm{NFW}(R) = \frac{4 \rho_\mathrm{crit} \delta_c r_s}{(R/r_s)^2} \left(
+% \begin{equation}\overline{\Sigma}_\mathrm{NFW}(R) = \frac{4 \rho_\mathrm{crit} \delta_c r_s}{(R/r_s)^2} \left(
 %     \frac{2}{\sqrt{(R/r_s)^2 - 1}} ~\arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) + \ln{\left(\frac{R/r_s}{2}\right)}
-% \right)\]
+% \right)
+% \end{equation}
 %
@@
 
-\[\Sigma_\mathrm{NFW}(\theta) = \frac{2 \rho_\mathrm{crit} \delta_c D_L \theta_s}{(\theta/\theta_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(\theta/\theta_s)^2 - 1}} \arctan\left(\sqrt{\frac{\theta/\theta_s - 1}{\theta/\theta_s + 1}} \right) \right)\]
+\begin{equation}
+\Sigma_\mathrm{NFW}(\theta) = \frac{2 \rho_\mathrm{crit} \delta_c D_L \theta_s}{(\theta/\theta_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(\theta/\theta_s)^2 - 1}} \arctan\left(\sqrt{\frac{\theta/\theta_s - 1}{\theta/\theta_s + 1}} \right) \right)
+\end{equation}
 
-\[\overline{\Sigma}_\mathrm{NFW}(\theta) = \frac{4 \rho_\mathrm{crit} \delta_c D_L \theta_s}{(\theta/\theta_s)^2} \left(
+\begin{equation}
+\overline{\Sigma}_\mathrm{NFW}(\theta) = \frac{4 \rho_\mathrm{crit} \delta_c D_L \theta_s}{(\theta/\theta_s)^2} \left(
     \frac{2}{\sqrt{(\theta/\theta_s)^2 - 1}} ~\arctan\left(\sqrt{\frac{\theta/\theta_s - 1}{\theta/\theta_s + 1}} \right) + \ln{\left(\frac{\theta/\theta_s}{2}\right)}
-\right)\]
+\right)
+\end{equation}
 
@@
 
-\[\gamma_\mathrm{NFW}(\theta) = \frac{\overline{\Sigma}_\mathrm{NFW}(\theta) - \Sigma_\mathrm{NFW}(\theta)}{\Sigma_\mathrm{crit}} \]
+\begin{equation}
+\gamma_\mathrm{NFW}(\theta) = \frac{\overline{\Sigma}_\mathrm{NFW}(\theta) - \Sigma_\mathrm{NFW}(\theta)}{\Sigma_\mathrm{crit}}
+\end{equation}
 
@@
 
-\[\delta_c = \frac{200}{3} \frac{c^3}{\ln(1 + c) - c/(1 + c)}\]
-\[r_s = \frac{r_{200}}{c}\]
-\[r_{200} = \left( \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}} \right)^{1/3}\]
-\[c = \frac{r_{200}}{r_s}\]
+\begin{equation}
+\delta_c = \frac{200}{3} \frac{c^3}{\ln(1 + c) - c/(1 + c)}
+\end{equation}
+\begin{equation}
+r_s = \frac{r_{200}}{c}
+\end{equation}
+\begin{equation}
+r_{200} = \left( \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}} \right)^{1/3}
+\end{equation}
+\begin{equation}
+c = \frac{r_{200}}{r_s}
+\end{equation}
 
@@
 The goal of this project is to devise a method to analyze lensed galaxy cluster data and find which density profile is more probable between the isothermal and NFW profiles.
+In order to do so, we generate simulated data sets and analyze them to find the more probable profiles they would fit into.
+This analysis method is expected to be usable in determining the characteristics of real observed data as well.
 
@@
 \section{Methods}
-\subsection{Calculation of Shear and Deflection Angles for Each Profile}
 
 \subsection{Modelling of Foreground Lens and Background Galaxies}
+Based on the calculations shown above, we have modelled singular lenses corresponding to each density profile.
+ Background galaxies have been generated via randomization of angular coordinates.
+
 \begin{enumerate}
@@
     \begin{itemize}
-        \item $z_L = 0.3$
-        \item $z_S = 1.0$
+        \item $z_L = 0.3$ (bullet cluster)
+        \item $z_S = 1.0$ (Hubble Deep Field)
         \item $M_{halo} = 10^{15} M_\odot$
@@
 \subsection{Generating Simulated Data}
-\begin{enumerate}
-\item Apply shear and deflection angle to background galaxies, get simulated data: $N$ sets of $\epsilon_1$, $\epsilon_2$, $\theta_1$, $\theta_2$
-\end{enumerate}
+We applied the shear and deflection angles to background galaxies to get simulated data: $N$ sets of $\epsilon_1$, $\epsilon_2$, $\theta_1$, $\theta_2$
 
@@
 
+Like (COMPARISONS BETWEEN ISOTHERMAL AND NFW MASS PROFILES
+FOR STRONG-LENSING GALAXY CLUSTERS), we find that the strong lensing regime provides the most
+But also, weak lensing can in fact provide sufficient distinguishability
+
 From our data analysis, we were able to find the more probable density profile of a simulated data set.
+Since the simulated data is based on the NFW and isothermal profile models, we were able to decisively distinguish between the two.
+When analyzing real observed data, we expect the probability ratios to be relatively more even.
 Future goals include the use of these methods to analyze observed data of galaxy clusters to find the density profile of their lenses.

### 2018-05-07 paper.tex
New figures

@@
 \usepackage{graphicx}
+\usepackage{amsmath}
 % \usepackage{txfonts}
@@
 We then describe the purpose of our project, to distinguish between NFW and isothermal profiles, in detail.
+The goal of this project is to devise a method to analyze lensed galaxy cluster data and find which density profile is more probable between the isothermal and NFW profiles.
+In order to do so, we generate simulated data sets and analyze them to find the more probable profiles they would fit into.
+This analysis method is expected to be usable in determining the characteristics of real observed data as well.
+
+Estimating ellipticity has well-documented issues [cite] due to noise and PSF
 
@@
 
+At small angles, we can assume from small angle approximations that $R = D_L \theta$.
+
 We also define the convergence, $\kappa$ to be
@@
 
+Strong lensing features take over when the convergence is greater than one.
 Tangential shear, along with the components of shear are shown as follows.
@@
 
+The tangential shear is decomposed into two components, $\gamma_1$ and $\gamma_2$. $\gamma_1$ represents stretching along the $\theta_x$ and $\theta_y$ axes, and $\gamma_2$
 \begin{equation}
-\gamma_1 = -\gamma_t \cos{2\phi}
+\begin{split}
+\gamma_1 = -\gamma_t \cos{2\phi}\\
 \gamma_2 = -\gamma_t \sin{2\phi}
+\end{split}
 \end{equation}
 
-It can be shown that for a spherical lens profile, the only component of shear should be the tangential shear, $\gamma_t$:
+It can be shown that for a spherical lens profile, the only component of shear $\gamma$ should be the tangential shear, $\gamma_t$:
 \citep{Dodelson2017}
@@
 \end{equation}
-
-At small angles, we can assume from small angle approximations that $R = D_L \theta$.
-
-Prove that spherical density profiles only have tangential shear and ellipticity
 
@@
 
+\begin{figure}
+    \includegraphics{isothermalproperties.pdf}
+    \caption{Lensing quantities for a CIS profile with $M_{200} = 10^{15} M_\odot$ and $r_c = 10$ kpc.}
+    \label{}
+\end{figure}
+
 \section{Navarro-Frenk-White (NFW) Profile}
@@
 \end{equation}
+
+What redshift is $\rho_\mathrm{crit}$ evaluated at? - at halo redshift - can we use current time?
 
@@
 
-Estimating ellipticity has well-documented issues [cite] due to noise and PSF
-
-\subsection{Project Purpose}
-The goal of this project is to devise a method to analyze lensed galaxy cluster data and find which density profile is more probable between the isothermal and NFW profiles.
-In order to do so, we generate simulated data sets and analyze them to find the more probable profiles they would fit into.
-This analysis method is expected to be usable in determining the characteristics of real observed data as well.
-
-\newpage
+\begin{figure}
+    \includegraphics{nfwproperties.pdf}
+    \caption{Lensing quantities for a NFW profile with $M_{200} = 10^{15} M_\odot$ and $c = 10$.}
+    \label{}
+\end{figure}
 
@@
 
+\begin{figure}
+    \includegraphics[width=0.49\textwidth]{isothermalellipticities.pdf}
+    \includegraphics[width=0.49\textwidth]{nfwellipticities.pdf}
+    \caption{plots}
+    \label{}
+\end{figure}
+
 \subsection{Data Analysis and Density Profile Determination}
@@
 
-\subsection{Questions}
-\begin{itemize}
-    \item How to properly do sigma contours?
-    \item What theta range should we look at? (5 arcminutes?)
-    \item What redshift is $\rho_\mathrm{crit}$ evaluated at? - at halo redshift - can we use current time?
-    \item Using $c = 10$?
-    \item Where to go from here?
-\end{itemize}
+What theta range should we look at? (5 arcminutes?)
+
+How to properly do sigma contours?
 
@@
 
+Where to go from here?
+
 \bibliographystyle{plainnat}

### 2018-05-07 analysis.py

@@ -5,7 +5,7 @@ import astropy.units as u
 from scipy.optimize import curve_fit
 from scipy.stats import binned_statistic
 from lensing import *
-np.random.seed(0)
+np.random.seed(1)
 
 ### DATA GENERATION ###
 galaxyNumberDensity = 50/u.arcmin**2

### 2018-05-07 figures.py

@@ -5,7 +5,7 @@ import astropy.units as u
 from scipy.optimize import curve_fit
 from scipy.stats import binned_statistic
 from lensing import *
-np.random.seed(0)
+np.random.seed(1)
 plt.rcParams["font.family"] = "serif"
 plt.rcParams["mathtext.fontset"] = "cm"
 plt.rcParams["text.usetex"] = True
@@ -59,26 +59,39 @@ print("theta_s:", halo_nfw.Ts.to(u.arcsec))
 
 
 backgroundGalaxies = [BackgroundGalaxy(
-    Bx=(viewSize*np.random.rand()-viewSize/2)*u.arcsec,
-    By=(viewSize*np.random.rand()-viewSize/2)*u.arcsec,
+    Bx=(viewSize*np.random.rand()-viewSize/2),
+    By=(viewSize*np.random.rand()-viewSize/2),
     e1=0,
     e2=0,
     DS=DS) for i in range(Ngal)]
 
-def lensingImage(halo, backgroundGalaxies, v, a=1):
+isolensedBackgroundGalaxies = [halo_iso.lense(gal) for gal in backgroundGalaxies]
+nfwlensedBackgroundGalaxies = [halo_nfw.lense(gal) for gal in backgroundGalaxies]
+
+
+def lensingImage(lensedBackgroundGalaxies, v, title):
     # Produce a mock lensing image with a halo and a population of background galaxies
     # v is the view width and a is the size of galaxies
+
+    theta_x = np.array([lgal.Tx.to_value(u.arcsec) for lgal in lensedBackgroundGalaxies]) * u.arcsec
+    theta_y = np.array([lgal.Ty.to_value(u.arcsec) for lgal in lensedBackgroundGalaxies]) * u.arcsec
+    e1 = np.array([lgal.e1.to_value("") for lgal in lensedBackgroundGalaxies])
+    e2 = np.array([lgal.e2.to_value("") for lgal in lensedBackgroundGalaxies])
+    phi = np.array([lgal.phi.to_value(u.rad) for lgal in lensedBackgroundGalaxies])
+    epsilon = -e1*np.cos(2*phi) - e2*np.sin(2*phi)
+
     fig = plt.figure()
-    ax = fig.add_subplot(111, aspect="equal")
-    ax.set_xlim(-v/2,v/2)
-    ax.set_ylim(-v/2,v/2)
-    for gal in backgroundGalaxies:
[…]

### 2018-05-07 lensing.py

@@ -7,8 +7,6 @@ import astropy.units as u
 import astropy.constants as const
 from cmath import sqrt as csqrt
 
-plt.style.use(astropy_mpl_style)
-plt.rcParams["figure.dpi"] = 100
 
 ### CONSTANTS ###
 c = const.c
@@ -123,11 +121,3 @@ class LensedBackgroundGalaxy:
         self.DS = DS
         self.T = np.sqrt(Tx**2 +Ty**2)
         self.phi = np.arctan2(Ty, Tx)
-
-    def ellipse(self, a):
-        # Returns matplotlib ellipse object of approximate size a
-        e = np.sqrt(self.e1**2 + self.e2**2)
-        return Ellipse(xy=[self.Tx.to_value(u.arcsec),self.Ty.to_value(u.arcsec)],
-                       width=a,
-                       height=a*(e+1)/(e-1),
-                       angle=self.phi.to_value(u.degree))

### 2018-05-07 paper.tex
new references and comparison figure, more paper writing

@@
 \graphicspath{ {figures/} }
+\linespread{1.3}
 
@@
 We examine the feasibility of distinguishing NFW and cored isothermal density profiles using weak gravitational lensing shear.
- To do so, we use Python to model lenses in the two different profiles, as well as background galaxies to be lensed.
+
+We model lenses in the two different profiles, as well as background galaxies to be lensed.
 Analyzing the simulated data of these lensed galaxies gives us insight into how we can distinguish the differences between the two profiles.
@@
 The principle is applicable on a large range of scales, from all-sky mass maps based on cosmic microwave background shear to studies of individual galaxies and clusters.
-A common use of lensing is
+In particular, by observing the coherent distortions of many background galaxies, the shear profile, and consequently the density profile of a foreground halo lens may be determined.
 
-Two commonly used density profiles in weak gravitational lensing are the isothermal profile and the Navarro-Frenk-White (NFW) profile.
+Two commonly used density profiles in the field are the isothermal profile and the Navarro-Frenk-White (NFW) profile.
+The NFW profile has been found to fit simulated dark matter halos very well \citep{}, while the isothermal profile .
+Both profiles have infinite extent
+
+Lensing offers one of the only ways to probe the distribution
+In this paper, we will investigate the distinguishability of
+given galaxy-galaxy lensing data
+
 We start with introducing the general characteristics of spherical density profiles, followed by cored isothermal and NFW profiles.
@@
 Consider such a spherically symmetric halo density profile $\rho(r)$
+
+The lens halo is located at an angular diameter distance $D_L$ from the observer and we want to consider its effects on a source object behind it at an angular diameter distance $D_S$.
 
@@
 \begin{equation}
-\Sigma_\mathrm{crit} = \frac{c^2}{4\pi G} \frac{D_S}{D_{SL} D_L}
+\Sigma_\mathrm{crit} = \frac{c^2}{4\pi G} \frac{D_S}{(D_S - D_L) D_L}
 \end{equation}
@@
 \section{Cored Isothermal Sphere Profile}
-The cored isothermal sphere (CIS) profile is related to the singular isothermal sphere, which is often used to describe halos and other collapsed astrophysical objects because of its simple formulation.
+The cored isothermal sphere (CIS) profile is related to the singular isothermal sphere profile, which is often used to describe halos and other collapsed astrophysical objects because of its simple formulation.
 Unlike the singular isothermal sphere, the cored isothermal sphere does not have a density singularity at its center due to a finite core radius $r_c$.
@@
 \begin{figure}
-    \includegraphics{isothermalproperties.pdf}
+    \centering
+    \includegraphics[width=0.8\textwidth]{isothermalproperties.pdf}
     \caption{Lensing quantities for a CIS profile with $M_{200} = 10^{15} M_\odot$ and $r_c = 10$ kpc.}
@@
 \begin{figure}
-    \includegraphics{nfwproperties.pdf}
+    \centering
+    \includegraphics[width=0.8\textwidth]{nfwproperties.pdf}
     \caption{Lensing quantities for a NFW profile with $M_{200} = 10^{15} M_\odot$ and $c = 10$.}
@@
     \begin{itemize}
-        \item Number density on sky: 50 galaxies/square arcminute
-        \item Intrinsic ellipticity drawn from Gaussian distribution with $\mu=0, \sigma=0.2$
+        \item Number density on sky: 50 galaxies/square arcminute (LSST, https://arxiv.org/pdf/1305.0793.pdf)
+        \item Intrinsic ellipticity drawn from Gaussian distribution with $\mu=0, \sigma=0.2$ (consistent with https://arxiv.org/pdf/1509.05058.pdf)
         \item Assume they are all that the same distance $D_S$ since this can be determined by redshift (neglecting some noise)
@@
         \item $z_L = 0.3$ (bullet cluster)
-        \item $z_S = 1.0$ (Hubble Deep Field)
+        \item $z_S = 1.0$ (Hubble Deep Field) (also consistent with https://arxiv.org/pdf/1509.05058.pdf)
+        we use the planck 2015 results
         \item $M_{halo} = 10^{15} M_\odot$
@@
 \begin{figure}
+    \centering
     \includegraphics[width=0.49\textwidth]{isothermalellipticities.pdf}
@@
 
-\section{Results and Conclusion}
+\section{Results}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.9\textwidth]{comparison.pdf}
+    \caption{plots}
+    \label{}
+\end{figure}
+
+\section{Conclusions}
 
@@
 But also, weak lensing can in fact provide sufficient distinguishability
+
+has been applied to observations before
+https://arxiv.org/pdf/astro-ph/9602053.pdf
+but not in the context of comparing density profiles using for strong and weak
+but this is highly dependent on good data
+
+http://iopscience.iop.org/article/10.1086/590049/pdf looked at NFW vs isothermal in strong lensing with a focus on arcs, and found differing levels of distinguishibility for different lenses.
+
+https://arxiv.org/pdf/1101.0650.pdf - our results don't match
 

### 2018-05-08 figures.py
Added intrinsic ellipticity to figures

@@ -61,8 +61,8 @@ print("theta_s:", halo_nfw.Ts.to(u.arcsec))
 backgroundGalaxies = [BackgroundGalaxy(
     Bx=(viewSize*np.random.rand()-viewSize/2),
     By=(viewSize*np.random.rand()-viewSize/2),
-    e1=0,
-    e2=0,
+    e1=np.random.normal(0, 0.2),
+    e2=np.random.normal(0, 0.2),
     DS=DS) for i in range(Ngal)]
 
 isolensedBackgroundGalaxies = [halo_iso.lense(gal) for gal in backgroundGalaxies]
@@ -77,19 +77,22 @@ def lensingImage(lensedBackgroundGalaxies, v, title):
     theta_y = np.array([lgal.Ty.to_value(u.arcsec) for lgal in lensedBackgroundGalaxies]) * u.arcsec
     e1 = np.array([lgal.e1.to_value("") for lgal in lensedBackgroundGalaxies])
     e2 = np.array([lgal.e2.to_value("") for lgal in lensedBackgroundGalaxies])
-    phi = np.array([lgal.phi.to_value(u.rad) for lgal in lensedBackgroundGalaxies])
+
+    # phi = np.array([lgal.phi.to_value(u.rad) for lgal in lensedBackgroundGalaxies])
+    # phi = np.arctan(theta_y/theta_x)
+    phi = np.arctan2(e2,e1)/2 + np.pi/2
     epsilon = -e1*np.cos(2*phi) - e2*np.sin(2*phi)
 
     fig = plt.figure()
     plt.gca().set_aspect("equal")
     plt.xlim(-v.to_value(u.arcsec)/2,v.to_value(u.arcsec)/2)
     plt.ylim(-v.to_value(u.arcsec)/2,v.to_value(u.arcsec)/2)
-    plt.quiver(theta_x, theta_y, -epsilon*np.sin(phi), epsilon*np.cos(phi), pivot="mid",
-        headwidth=0, width=.001)
+    plt.quiver(theta_x, theta_y, -epsilon*np.sin(phi), epsilon*np.cos(phi),
+        pivot="mid", headwidth=0, width=.001)
     plt.xlabel("$\\theta_x$ ($^{\prime\prime}$)")
     plt.ylabel("$\\theta_y$ ($^{\prime\prime}$)")
     plt.title(title)
-    plt.savefig(title.lower() + "ellipticities.pdf", bbox_inches="tight")
[…]

### 2018-05-08 figures.py
Updated actual figures with intrinsic ellipticity

@@ -92,7 +92,7 @@ def lensingImage(lensedBackgroundGalaxies, v, title):
     plt.xlabel("$\\theta_x$ ($^{\prime\prime}$)")
     plt.ylabel("$\\theta_y$ ($^{\prime\prime}$)")
     plt.title(title)
-    # plt.savefig(title.lower() + "ellipticities.pdf", bbox_inches="tight")
+    plt.savefig("figures/" + title.lower() + "ellipticities.pdf", bbox_inches="tight")
     plt.show()
 
 

### 2018-05-08 analysis.py
Put data generator code in datagenerator.py

@@ -1,89 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-import astropy.cosmology as cosmology
-import astropy.units as u
-from scipy.optimize import curve_fit
-from scipy.stats import binned_statistic
-from lensing import *
-np.random.seed(1)
-
-### DATA GENERATION ###
-galaxyNumberDensity = 50/u.arcmin**2
-viewSize = 1000*u.arcsec
-Ngal = round((viewSize**2 * galaxyNumberDensity).to_value(""))
-zS = 1.0
-zL = 0.3
-DS = cosmology.Planck15.comoving_distance(zS) / (1 + zS)
-DL = cosmology.Planck15.comoving_distance(zL) / (1 + zL)
-
-lensHalo = NFWHalo(
-    M200=1e15*u.solMass,
-    C=10,
-    DL=DL)
-
-backgroundGalaxies = [BackgroundGalaxy(
-    Bx=(viewSize*np.random.rand() - viewSize/2),
-    By=(viewSize*np.random.rand() - viewSize/2),
-    e1=np.random.normal(0, 0.2),
-    e2=np.random.normal(0, 0.2),
-    DS=DS) for i in range(Ngal)]
-
-lensedBackgroundGalaxies = [lensHalo.lense(gal) for gal in backgroundGalaxies]
-
-theta_x = np.array([lgal.Tx.to_value(u.arcsec) for lgal in lensedBackgroundGalaxies]) * u.arcsec
-theta_y = np.array([lgal.Ty.to_value(u.arcsec) for lgal in lensedBackgroundGalaxies]) * u.arcsec
-e1 = np.array([lgal.e1.to_value("") for lgal in lensedBackgroundGalaxies])
-e2 = np.array([lgal.e2.to_value("") for lgal in lensedBackgroundGalaxies])
-phi = np.array([lgal.phi.to_value(u.rad) for lgal in lensedBackgroundGalaxies])
-
-
-### ANALYSIS ###
-
-# Assume we have a dataset of N galaxies with positions (theta_x, theta_y) and ellipticities (e1, e2)
-# Assume they all have same known DS and DL
-# Assume these are numpy arrays of length N
-
-# Calculate radial position theta and magnitude of ellipticity epsilon
-theta = np.sqrt(theta_x**2 + theta_y**2)
-epsilon = -e1*np.cos(2*phi) - e2*np.sin(2*phi)
-# Create theta bins
[…]

### 2018-05-08 datagenerator.py

@@ -1,50 +1,89 @@
-"""
-Created by Doyee Byun
-April 10, 2018
-
-Goals:
-Figure out how to create data using code from lensing.py
-define initial conditions for creating data
-galaxy locations, lens profile, etc.
-"""
-
 import numpy as np
 import matplotlib.pyplot as plt
-from matplotlib.patches import Ellipse
 import astropy.cosmology as cosmology
-from astropy.visualization import astropy_mpl_style
 import astropy.units as u
-import astropy.constants as const
+from scipy.optimize import curve_fit
+from scipy.stats import binned_statistic
+from lensing import *
+np.random.seed(0)
 
-#import profiles from lensing.py
-from lensing import NFWHalo
-from lensing import IsothermalHalo
-from lensing import BackgroundGalaxy
+### DATA GENERATION ###
+galaxyNumberDensity = 50/u.arcmin**2
+viewSize = 1000*u.arcsec
+Ngal = round((viewSize**2 * galaxyNumberDensity).to_value(""))
+zS = 1.0
+zL = 0.3
+DS = cosmology.Planck15.comoving_distance(zS) / (1 + zS)
+DL = cosmology.Planck15.comoving_distance(zL) / (1 + zL)
 
-# data format is theta_x, theta_y, e1, e2
+lensHalo = NFWHalo(
+    M200=1e15*u.solMass,
+    C=10,
+    DL=DL)
 
-#test parameters for lens
-M200_0 = 100*u.solMass
-c_param = 0.5
-dl = 1*u.Gpc
-
-datafile = open('output1.txt','w')
-nfw_1 = NFWHalo(M200_0,c_param,dl)
-
-#Sample NFW lensed galaxy data made with rand().
-#More deliberate placing of galaxies can be done if found necessary
 backgroundGalaxies = [BackgroundGalaxy(
-    Bx=(100*np.random.rand()-50)*u.arcsec,
-    By=(100*np.random.rand()-50)*u.arcsec,
-    e1=0,
-    e2=0,
-    a=1*u.arcsec,
-    DS=10*u.Gpc) for i in range(300)]
-for i in range(0,len(backgroundGalaxies)):
-    newGalx = nfw_1.lense(backgroundGalaxies[i])
-    datafile.write(str(newGalx.Tx)+"\t"+str(newGalx.Ty)+"\t"+str(newGalx.e1)+"\t"+str(newGalx.e2)+"\t\n")
[…]

### 2018-05-08 datagenerator.py
Added correct angular diameter distances for DSL

@@ -13,8 +13,9 @@ viewSize = 1000*u.arcsec
 Ngal = round((viewSize**2 * galaxyNumberDensity).to_value(""))
 zS = 1.0
 zL = 0.3
-DS = cosmology.Planck15.comoving_distance(zS) / (1 + zS)
-DL = cosmology.Planck15.comoving_distance(zL) / (1 + zL)
+DS = cosmology.Planck15.angular_diameter_distance(zS)
+DL = cosmology.Planck15.angular_diameter_distance(zL)
+DSL = cosmology.Planck15.angular_diameter_distance_z1z2(zL, zS)
 
 lensHalo = NFWHalo(
     M200=1e15*u.solMass,

### 2018-05-08 figures.py

@@ -12,14 +12,16 @@ plt.rcParams["text.usetex"] = True
 plt.rcParams["figure.dpi"] = 150
 
 
-# here is an example of lensing very close to the halo
+# An example of lensing very close to the halo
 galaxyNumberDensity = 1000/(100*u.arcsec)**2
 viewSize = 100*u.arcsec
 Ngal = round((viewSize**2 * galaxyNumberDensity).to_value(""))
 zS = 1.0
 zL = 0.3
-DS = cosmology.Planck15.comoving_distance(zS) / (1 + zS)
-DL = cosmology.Planck15.comoving_distance(zL) / (1 + zL)
+DS = cosmology.Planck15.angular_diameter_distance(zS)
+DL = cosmology.Planck15.angular_diameter_distance(zL)
+DSL = cosmology.Planck15.angular_diameter_distance_z1z2(zL, zS)
+
 
 halo_iso = IsothermalHalo(
     M200=1e15*u.solMass,

### 2018-05-08 lensing.py

@@ -15,12 +15,11 @@ H0 = cosmology.Planck15.H0
 RHO_CRIT = 3 * H0**2 / (8 * np.pi * G) # only use rho_crit at current time
 u.set_enabled_equivalencies(u.dimensionless_angles()) # allow angles to be dimensionless
 
-
-### USEFUL FUNCTIONS ###
-
 def SIGMA_CRIT(DS, DL):
     # Critical surface density for lens at distance DL and source at distance DS
-    DSL = DS - DL
+    zS = cosmology.z_at_value(cosmology.Planck15.angular_diameter_distance, DS, zmax=1.1)
+    zL = cosmology.z_at_value(cosmology.Planck15.angular_diameter_distance, DL, zmax=1.1)
+    DSL = cosmology.Planck15.angular_diameter_distance_z1z2(zL, zS)
     return c**2 / (4 * np.pi * G) * (DS / (DSL * DL))
 
 

### 2018-05-08 figures.py
Comments

@@ -5,7 +5,7 @@ import astropy.units as u
 from scipy.optimize import curve_fit
 from scipy.stats import binned_statistic
 from lensing import *
-np.random.seed(1)
+np.random.seed(0)
 plt.rcParams["font.family"] = "serif"
 plt.rcParams["mathtext.fontset"] = "cm"
 plt.rcParams["text.usetex"] = True
@@ -22,7 +22,6 @@ DS = cosmology.Planck15.angular_diameter_distance(zS)
 DL = cosmology.Planck15.angular_diameter_distance(zL)
 DSL = cosmology.Planck15.angular_diameter_distance_z1z2(zL, zS)
 
-
 halo_iso = IsothermalHalo(
     M200=1e15*u.solMass,
     rc=10*u.kpc,
@@ -32,6 +31,8 @@ halo_nfw = NFWHalo(
     M200=1e15*u.solMass,
     C=10,
     DL=DL)
+
+### Plot of halo lensing properties ###
 
 def plotProperties(halo, start, stop, step, DS, name):
     # Plot the shear, ellipticity, convergence, and magnification for the halo
@@ -59,6 +60,8 @@ print("theta_0:", halo_iso.T0(DS).to(u.arcsec))
 plotProperties(halo_nfw, 0.01*u.arcsec, viewSize, 500, DS, "nfwproperties")
 print("theta_s:", halo_nfw.Ts.to(u.arcsec))
 
+
+### Graphic of lensed galaxy ellipticities ###
 
 backgroundGalaxies = [BackgroundGalaxy(
     Bx=(viewSize*np.random.rand()-viewSize/2),

### 2018-05-08 paper.tex
Added intrinsic ellipticity to figures
Merge subsection of generating data into modelling background

@@
         \item Assume they are all that the same distance $D_S$ since this can be determined by redshift (neglecting some noise)
+        \item Apply shear and deflection angles to background galaxies to get simulated data: $N$ sets of $\epsilon_1$, $\epsilon_2$, $\theta_1$, $\theta_2$
     \end{itemize}
@@
 \end{enumerate}
-
-\subsection{Generating Simulated Data}
-We applied the shear and deflection angles to background galaxies to get simulated data: $N$ sets of $\epsilon_1$, $\epsilon_2$, $\theta_1$, $\theta_2$
 
@@
 
+ignore cosmic shear (https://journals.aps.org/prd/pdf/10.1103/PhysRevD.70.023008)
+
 From our data analysis, we were able to find the more probable density profile of a simulated data set.

### 2018-05-08 datagenerator.py
Changed seed

@@ -5,7 +5,7 @@ import astropy.units as u
 from scipy.optimize import curve_fit
 from scipy.stats import binned_statistic
 from lensing import *
-np.random.seed(0)
+np.random.seed(10)
 
 ### DATA GENERATION ###
 galaxyNumberDensity = 50/u.arcmin**2
@@ -36,13 +36,6 @@ theta_y = np.array([lgal.Ty.to_value(u.arcsec) for lgal in lensedBackgroundGalax
 e1 = np.array([lgal.e1.to_value("") for lgal in lensedBackgroundGalaxies])
 e2 = np.array([lgal.e2.to_value("") for lgal in lensedBackgroundGalaxies])
 phi = np.array([lgal.phi.to_value(u.rad) for lgal in lensedBackgroundGalaxies])
-
-
-### ANALYSIS ###
-
-# Assume we have a dataset of N galaxies with positions (theta_x, theta_y) and ellipticities (e1, e2)
-# Assume they all have same known DS and DL
-# Assume these are numpy arrays of length N
 
 # Calculate radial position theta and magnitude of ellipticity epsilon
 theta = np.sqrt(theta_x**2 + theta_y**2)

### 2018-05-08 figures.py

@@ -5,7 +5,7 @@ import astropy.units as u
 from scipy.optimize import curve_fit
 from scipy.stats import binned_statistic
 from lensing import *
-np.random.seed(0)
+np.random.seed(10)
 plt.rcParams["font.family"] = "serif"
 plt.rcParams["mathtext.fontset"] = "cm"
 plt.rcParams["text.usetex"] = True
@@ -42,9 +42,10 @@ def plotProperties(halo, start, stop, step, DS, name):
     kappa = np.array([(halo.surfaceDensity(t) / SIGMA_CRIT(DS, halo.DL)).to_value("") for t in theta])
     mu = 1/((1-kappa)**2 - gamma**2)
     plt.figure()
-    plt.plot(theta, epsilon)
-    plt.plot(theta, gamma)
-    plt.plot(theta, kappa)
+    plt.grid()
+    plt.plot(theta, epsilon, c="#3799CE")
+    plt.plot(theta, gamma, c="#21893B")
+    plt.plot(theta, kappa, c="#B00728")
     # plt.plot(theta, mu)
     plt.legend(["$\epsilon$", "$\gamma$", "$\kappa$", "$\mu$"])
     plt.xlabel("$\\theta$ ($^{\prime\prime}$)")

### 2018-05-08 lensing.py

@@ -2,7 +2,6 @@ import numpy as np
 import matplotlib.pyplot as plt
 from matplotlib.patches import Ellipse
 import astropy.cosmology as cosmology
-from astropy.visualization import astropy_mpl_style
 import astropy.units as u
 import astropy.constants as const
 from cmath import sqrt as csqrt
@@ -51,7 +50,7 @@ class Halo:
         T = np.sqrt(Tx**2 + Ty**2)
         phi = np.arctan2(Ty, Tx)
         e = self.ellipticity(T, galaxy.DS)
-        e1 = galaxy.e1 - e*np.cos(2*phi) # TODO: how do ellipticities add?
+        e1 = galaxy.e1 - e*np.cos(2*phi)
         e2 = galaxy.e2 - e*np.sin(2*phi)
         return LensedBackgroundGalaxy(Tx, Ty, e1, e2, galaxy.DS)
 

### 2018-05-08 paper.tex
commented out questions
Paper: general lensing

@@
 \section{Introduction}
-Gravitational lensing allows us to investigate the matter density distributions of cosmic objects by observing the characteristic distortions imparted on other objects in the background.
-The principle is applicable on a large range of scales, from all-sky mass maps based on cosmic microwave background shear to studies of individual galaxies and clusters.
+Gravitational lensing allows us to investigate the matter density distributions of cosmic objects by observing the characteristic light distortions imparted on other objects in the background.
+The principle is applicable on a large range of scales, from all-sky mass maps based on cosmic microwave background shear, to studies of individual galaxies and clusters.
 In particular, by observing the coherent distortions of many background galaxies, the shear profile, and consequently the density profile of a foreground halo lens may be determined.
@@
 Two commonly used density profiles in the field are the isothermal profile and the Navarro-Frenk-White (NFW) profile.
-The NFW profile has been found to fit simulated dark matter halos very well \citep{}, while the isothermal profile .
-Both profiles have infinite extent
+The NFW profile has been found to fit simulated dark matter halos very well \citep{}, while the isothermal profile results from an idealized isothermal collapse \citep{}.
+Both profiles extend to infinity
 
-Lensing offers one of the only ways to probe the distribution
-In this paper, we will investigate the distinguishability of
+It is of great interest to determine the general forms of halo density profiles
+since this tells us about structure formation and the nature of dark matter
+\citep{}
+Lensing offers one of the few ways to probe the distribution of all matter, not just baryonic matter.
+rotation curve present difficulties (https://arxiv.org/pdf/astro-ph/0201352.pdf)
+
+In this paper, we will investigate the distinguishability of NFW and isothermal profiles
 given galaxy-galaxy lensing data
-
-We start with introducing the general characteristics of spherical density profiles, followed by cored isothermal and NFW profiles.
-We then describe the purpose of our project, to distinguish between NFW and isothermal profiles, in detail.
 The goal of this project is to devise a method to analyze lensed galaxy cluster data and find which density profile is more probable between the isothermal and NFW profiles.
@@
 
-Estimating ellipticity has well-documented issues [cite] due to noise and PSF
+Outline:
+We start by introducing the general lensing characteristics of spherical density profiles, followed by the specifics for cored isothermal and NFW profiles. We then describe
+The results
 
-We describe the common characteristics of spherical density profiles.
-Here we define our conventions for various lensing quantities, which mainly conform to those used by \citet{Dodelson2017}. We use the thin lens approximation and assume spherical lens profiles.
-Consider such a spherically symmetric halo density profile $\rho(r)$
-
-The lens halo is located at an angular diameter distance $D_L$ from the observer and we want to consider its effects on a source object behind it at an angular diameter distance $D_S$.
-
-The projected surface density at radius R on the projected plane is defined, considering the z axis to be along the line of sight:
+\subsection{Lensing by a spherical lens profile}
+Here we define our conventions for various lensing quantities, which mainly conform to those used by \citet{Dodelson2017}.
+We use the thin lens approximation and assume spherical lens profiles.
+Consider such a spherically symmetric halo density profile $\rho(r)$ acting as a gravitational lens.
+This lens halo is located at an angular diameter distance $D_L$ from the observer and we want to find out how it affects a source object behind it at an angular diameter distance $D_S$.
+Set the $z$ axis to be along the line of sight, and use local cylindrical coordinates $R$, $\phi$, and $z$.
+The projected surface density $\Sigma$ at radius $R$ on the projected plane is obtained by integrating the density over the entire $z$ axis:
 \begin{equation}
@@
 \end{equation}
-
-An important related measure in gravitational lensing is the average projected surface density within radius R:
+A useful related measure in gravitational lensing is the average projected surface density within a radius $R$:
 \begin{equation}
@@
 \end{equation}
-
-The critical surface density marks the typical boundary between what is considered strong and weak lensing:
+The critical surface density is an important quantity that marks the typical boundary between what is considered strong and weak lensing:
 \begin{equation}
-\Sigma_\mathrm{crit} = \frac{c^2}{4\pi G} \frac{D_S}{(D_S - D_L) D_L}
+\Sigma_\mathrm{crit} = \frac{c^2}{4\pi G} \frac{D_S}{D_{SL} D_L}
 \end{equation}
 
-At small angles, we can assume from small angle approximations that $R = D_L \theta$.
+$D_S$ and $D_L$ are calculated like normal angular diameter distances in a flat expanding universe: $D = \chi(z)/(1 + z)$, where $\chi(z)$ is the comoving distance to redshift $z$.
+The redshift $z$ of an object, such as a halo lens or a background galaxy, is typically easy to measure.
+Note that $D_{SL}$ is nominally the distance from the source to the lens, but since it is an angular diameter distance, it is calculated as $D_{SL} = (\chi_S - \chi_L)/(1 + z_S)$.
 
-We also define the convergence, $\kappa$ to be
+All relevant angles in this problem are small, so we can assume that $R = D_L \theta$, where $\theta$ is the angular position on the observer's sky, with the halo center at the origin.
+This may be represented as the vector $\vec{\theta}$, but in the spherically symmetric case, the magnitude $\theta$ is sufficient.
+Thus we can easily change variables in all lensing quantities from $R$ to $\theta$.
+
+We define the convergence $\kappa$ at angular position $\theta$ as the ratio of surface density to critical surface density.
+Strong lensing phenomena such as arcs, rings, multiple images, and magnification are dominant when the convergence is greater than 1, or the projected surface density is greater than the critical surface density.
 \begin{equation}
@@
 \end{equation}
-
-Strong lensing features take over when the convergence is greater than one.
-Tangential shear, along with the components of shear are shown as follows.
+While the convergence determines how an object is uniformly scaled or magnified by a gravitational lens, another quantity, shear, describes the stretching of images along an axis.
+Shear is usually expressed as two components, $\gamma_1$ and $\gamma_2$.
+The tangential shear $\gamma_t$ is the component of stretching in the $\hat{\phi}$ direction.
+It can be shown that for a spherical lens profile, the only component of shear $\gamma$ should be the tangential shear, $\gamma_t$.
+For a spherical lens, tangential shear can be shown to be simply related to the convergence and average convergence \citep{Dodelson2017}:
 \begin{equation}
@@
 \end{equation}
-
-The tangential shear is decomposed into two components, $\gamma_1$ and $\gamma_2$. $\gamma_1$ represents stretching along the $\theta_x$ and $\theta_y$ axes, and $\gamma_2$
+The tangential shear is decomposed into two components, $\gamma_1$ and $\gamma_2$.
+$\gamma_1$ represents stretching along the $\theta_x$ and $\theta_y$ axes, and $\gamma_2$ represents stretching along the $\theta_y = \theta_x$ and $\theta_y = - \theta_x$ lines.
+They can be obtained through a relation with $\gamma_t$ and the cylindrical azimuthal angle $\phi$.
 \begin{equation}
@@
 \end{equation}
-
-It can be shown that for a spherical lens profile, the only component of shear $\gamma$ should be the tangential shear, $\gamma_t$:
-\citep{Dodelson2017}
+The shear magnitude, which is equal to tangential shear, also follows from trigonometric identities:
 \begin{equation}
-\gamma = \gamma_t = \sqrt{{\gamma_1}^2 + {\gamma_2}^2} = -\gamma_1 \cos{2\phi} -\gamma_2 \sin{2\phi}
+\gamma = \gamma_t = -\gamma_1 \cos{2\phi} -\gamma_2 \sin{2\phi}
 \end{equation}
 
-Deflection angle is
+Changes in object shapes due to lensing can be quantified using the ellipticity $\epsilon$.
+This is most commonly used in weak lensing, where shape changes are best described by simple stretching.
+Ellipticity is defined using the semimajor axis $a$ and semiminor axis $b$ of an ellipse \citep{Narayan1996}:
 \begin{equation}
-\vec{\alpha}(\vec{\theta}) = \overline{\kappa}(\theta)\vec{\theta}
+\epsilon = \frac{a^2 - b^2}{a^2 + b^2}
 \end{equation}
-\begin{equation}
-\vec{\beta} = \vec{\theta} - \vec{\alpha} = (1 - \overline{\kappa}(\theta))\vec{\theta}
-\end{equation}
-
-while ellipticity is
+Like shear, there are two components of ellipticity, $\epsilon_1$ and $\epsilon_2$, which are analogous to the shear components $\gamma_1$ and $\gamma_2$.
+The ellipticity that would be induced in an otherwise perfectly circular object is:
 \begin{equation}
@@
 \end{equation}
+And there is an analogous ellipticity magnitude or tangential ellipticity:
 \begin{equation}
@@
 
-\section{Cored Isothermal Sphere Profile}
+Gravitational lensing causes a deflection in the observed image position of background objects.
+If the true position of the object is $\vec{\beta}$ and it appears at position $\vec{\theta}$, then the deflection angle is defined:
+\begin{equation}
+\vec{\alpha}(\vec{\theta}) = \overline{\kappa}(\theta)\vec{\theta}
+\end{equation}
+From this expression, it can be seen that deflection is most significant in the strong lensing regime, where $\kappa > 1$.
+
+\subsection{Cored Isothermal Sphere Profile}
 The cored isothermal sphere (CIS) profile is related to the singular isothermal sphere profile, which is often used to describe halos and other collapsed astrophysical objects because of its simple formulation.
@@
 
-\section{Navarro-Frenk-White (NFW) Profile}
+\subsection{Navarro-Frenk-White (NFW) Profile}
 
@@
 
-What redshift is $\rho_\mathrm{crit}$ evaluated at? - at halo redshift - can we use current time?
+%What redshift is $\rho_\mathrm{crit}$ evaluated at? - at halo redshift - can we use current time?
 
@@
 
-Can calculate ellipticities from tangential shear.
+We can calculate ellipticities from tangential shear.
 
@@
 
+Estimating ellipticity has well-documented issues [cite] due to noise and PSF
+
 \begin{figure}
@@
 
-What theta range should we look at? (5 arcminutes?)
+%What theta range should we look at? (5 arcminutes?)
 
-How to properly do sigma contours?
+%How to properly do sigma contours?
 
@@
 \end{figure}
+
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=0.49\textwidth]{isothermalfitparams.pdf}
+%     \includegraphics[width=0.49\textwidth]{nfwfitparams.pdf}
+%     \caption{plots}
+%     \label{}
+% \end{figure}
 
@@
 
-Where to go from here?
+%Where to go from here?
 

### 2018-05-08 figures.py

@@ -42,7 +42,7 @@ def plotProperties(halo, start, stop, step, DS, name):
     kappa = np.array([(halo.surfaceDensity(t) / SIGMA_CRIT(DS, halo.DL)).to_value("") for t in theta])
     mu = 1/((1-kappa)**2 - gamma**2)
     plt.figure()
-    plt.grid()
+    plt.grid(color="#EEEEEE")
     plt.plot(theta, epsilon, c="#3799CE")
     plt.plot(theta, gamma, c="#21893B")
     plt.plot(theta, kappa, c="#B00728")

### 2018-05-08 paper.tex
Finished general lensing section

@@
 The projected surface density $\Sigma$ at radius $R$ on the projected plane is obtained by integrating the density over the entire $z$ axis:
-\begin{equation}
+\begin{equation} \label{sigma}
 \Sigma(R) = \int_{-\infty}^{\infty}{dz\ \rho(\sqrt{R^2 + z^2})}
@@
 A useful related measure in gravitational lensing is the average projected surface density within a radius $R$:
-\begin{equation}
+\begin{equation} \label{sigmabar}
 \overline{\Sigma}(R) = \frac{1}{\pi R^2} \int_0^{2\pi}{d\phi \int_0^{R}{dR'~\Sigma(R')R'}}
@@
 The critical surface density is an important quantity that marks the typical boundary between what is considered strong and weak lensing:
-\begin{equation}
+\begin{equation} \label{sigmacrit}
 \Sigma_\mathrm{crit} = \frac{c^2}{4\pi G} \frac{D_S}{D_{SL} D_L}
@@
 Strong lensing phenomena such as arcs, rings, multiple images, and magnification are dominant when the convergence is greater than 1, or the projected surface density is greater than the critical surface density.
-\begin{equation}
+\begin{equation} \label{convergence}
 \kappa(\theta) = \frac{\Sigma(\theta)}{\Sigma_\mathrm{crit}}
@@
 For a spherical lens, tangential shear can be shown to be simply related to the convergence and average convergence \citep{Dodelson2017}:
-\begin{equation}
+\begin{equation} \label{tangentialshear}
 \gamma_t(\theta) = \overline{\kappa}(\theta) - \kappa(\theta)
@@
 The ellipticity that would be induced in an otherwise perfectly circular object is:
-\begin{equation}
+\begin{equation} \label{ellipticity}
 \epsilon_i = \frac{2 \gamma_i/(1 - \kappa)}{1 + \gamma^2/(1 - \kappa)^2}
@@
 \subsection{Cored Isothermal Sphere Profile}
-The cored isothermal sphere (CIS) profile is related to the singular isothermal sphere profile, which is often used to describe halos and other collapsed astrophysical objects because of its simple formulation.
+The cored isothermal sphere (CIS) profile is related to the singular isothermal sphere (SIS) profile, which is often used to describe halos and other collapsed astrophysical objects because of its simple formulation.
 Unlike the singular isothermal sphere, the cored isothermal sphere does not have a density singularity at its center due to a finite core radius $r_c$.
-The CIS density profile is defined:
+The CIS density profile is defined
+\begin{equation} \label{cisdensity}
+\rho_\mathrm{CIS}(r) = \frac{\sigma^2}{2\pi G (r^2 + {r_c}^2)},
+\end{equation}
+where $\sigma^2$ is the velocity dispersion of the halo \citep{Chen2005, Shapiro1999}.
+Applying equation \ref{sigma} and defining $\theta_c = r_c/D_L$, we get the projected surface density of the CIS profile:
+\begin{equation}
+\Sigma_\mathrm{CIS}(\theta) = \frac{\sigma^2}{2 G D_L \sqrt{\theta^2 + {\theta_c}^2}}
+\end{equation}
+The average surface density inside angular radius $\theta$ is derived using equation \ref{sigmabar}:
+\begin{equation}
+\overline{\Sigma}_\mathrm{CIS}(\theta) = \frac{\sigma^2 \left(\sqrt{\theta^2 + {\theta_c}^2} - \theta_c \right)}{G D_L \theta^2}
+\end{equation}
+The tangential shear follows from equation \ref{tangentialshear}:
+\begin{equation}
+\gamma_\mathrm{CIS}(\theta) = \frac{\sigma^2 \left(\sqrt{\theta^2 + {\theta_c}^2} - \theta_c \right)}{\Sigma_\mathrm{crit} G D_L \theta^2} - \frac{\sigma^2}{2 \Sigma_\mathrm{crit} G D_L \sqrt{\theta^2 + {\theta_c}^2}}
+\end{equation}
+The ellipticity equations, while not quite elegant, are trivial to calculate from the shear.
 
+Although the total mass of the CIS profile diverges, we will use a common convention for quantifying the mass of the profile within a reasonable radius.
+We define $r_{200}$ as the radius at which the average enclosed density of the profile is 200 times the critical density of the universe.
+The critical density $\rho_\mathrm{crit}$ depends on cosmological parameters such as the Hubble constant $H_0$.
+We choose to use the critical density at the current time $\rho_\mathrm{crit,0}$ for all halos regardless of their redshift.
+We assume a flat $\Lambda$CDM universe and use the Planck 2015 results for all cosmological calculations \citep{PlanckCollaboration2015}.
+
+We define $M_{200}$ as the total mass enclosed within $r_{200}$:
 \begin{equation}
-\rho_\mathrm{iso}(r) = \frac{\sigma^2}{2\pi G (r^2 + {r_c}^2)}
+M_{200} = 200 \rho_\mathrm{crit} \frac{4}{3} \pi {r_{200}}^3
 \end{equation}
-
-where $\sigma^2$ is the velocity dispersion.
-https://arxiv.org/pdf/astro-ph/9810164.pdf
-% \begin{equation}\Sigma_\mathrm{iso}(R) = \frac{\sigma^2}{2 G \sqrt{R^2 + {r_c}^2}}
-% \end{equation}
-%
-% \begin{equation}\overline{\Sigma}_\mathrm{iso}(R) = \frac{\sigma^2 \left(\sqrt{R^2 + {r_c}^2} - r_c \right)}{G R^2}
-% \end{equation}
-%
-% In terms of angles:
-
-\begin{equation}
-\Sigma_\mathrm{iso}(\theta) = \frac{\sigma^2}{2 G D_L \sqrt{\theta^2 + {\theta_c}^2}}
+We also calculate $M_{200}$ specifically for a CIS profile by integrating equation \ref{cisdensity}:
+\begin{equation} \label{cisM200}
+M_{200} = M_\mathrm{enc}(r_{200}) = \frac{2 \sigma^2}{G} \left( r_{200} - r_c \arctan{\left(\frac{r_{200}}{r_c}\right)} \right)
 \end{equation}
-
-\begin{equation}
-\overline{\Sigma}_\mathrm{iso}(\theta) = \frac{\sigma^2 \left(\sqrt{\theta^2 + {\theta_c}^2} - \theta_c \right)}{G D_L \theta^2}
+Solving for $r_{200}$:
+\begin{equation} \label{r200}
+r_{200} = \left( \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}} \right)^{1/3}
 \end{equation}
-
-\begin{equation}
-\gamma_\mathrm{iso}(\theta) = \frac{\sigma^2 \left(\sqrt{\theta^2 + {\theta_c}^2} - \theta_c \right)}{\Sigma_\mathrm{crit} G D_L \theta^2} - \frac{\sigma^2}{2 \Sigma_\mathrm{crit} G D_L \sqrt{\theta^2 + {\theta_c}^2}}
-\end{equation}
-
-We switch dependence from $\sigma^2$ to $M_{200}$ with:
-
+We can now completely switch the CIS profile's dependence from $\sigma^2$ to $M_{200}$ with equation \ref{r200} and solving for $\sigma^2$ from equation \ref{cisM200}:
 \begin{equation}
@@
 
-This is derived from the definition of $M_{200}$:
-
-\begin{equation}
-M_{200} = 200 \rho_\mathrm{crit} \frac{4}{3} \pi {r_{200}}^3
-\end{equation}
-\begin{equation}
-M_{200} = M_\mathrm{enc}(r_{200}) = \frac{2 \sigma^2}{G} \left( r_{200} - r_c \arctan{\left(\frac{r_{200}}{r_c}\right)} \right)
-\end{equation}
-\begin{equation}
-r_{200} = \left( \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}} \right)^{1/3}
-\end{equation}
-
-The ellipticity equations, while not quite elegant, are trivial to calculate from the shear.
+Figure \ref{cisproperties} shows the convergence, tangential shear, and ellipticity of a Milky Way-sized halo lens at redshift 0.3 for lensed objects at redshift 1.
 
@@
     \includegraphics[width=0.8\textwidth]{isothermalproperties.pdf}
-    \caption{Lensing quantities for a CIS profile with $M_{200} = 10^{15} M_\odot$ and $r_c = 10$ kpc.}
-    \label{}
+    \caption{Lensing quantities for a CIS profile with $M_{200} = 10^{15} M_\odot$ and $r_c = 10$ kpc. $z_L = 0.3$ and $z_S = 1.0$.}
+    \label{cisproperties}
 \end{figure}

### 2018-05-08 paper.tex
Finished CIS section

@@
 \begin{equation}
-\gamma_\mathrm{CIS}(\theta) = \frac{\sigma^2 \left(\sqrt{\theta^2 + {\theta_c}^2} - \theta_c \right)}{\Sigma_\mathrm{crit} G D_L \theta^2} - \frac{\sigma^2}{2 \Sigma_\mathrm{crit} G D_L \sqrt{\theta^2 + {\theta_c}^2}}
+\gamma_\mathrm{CIS}(\theta) = \frac{\sigma^2}{\Sigma_\mathrm{crit} G D_L} \left(\frac{\sqrt{\theta^2 + {\theta_c}^2} - \theta_c}{\theta^2} - \frac{1}{2 \sqrt{\theta^2 + {\theta_c}^2}}\right)
 \end{equation}
-The ellipticity equations, while not quite elegant, are trivial to calculate from the shear.
+The ellipticity equation, while not quite elegant, is trivial to calculate using equation \ref{ellipticity}.
 
@@
 \subsection{Navarro-Frenk-White (NFW) Profile}
-
+The NFW profile has had some success in describing dark matter halos is both simulations and observations, though
+\citep{Navarro1997}
 \begin{equation}

### 2018-05-08 paper.tex
Shortened author list of reference paper
added preliminary text to results section
Switched to aasjournal citation style

@@
 \usepackage{microtype}
-\usepackage{natbib}
+\usepackage[square]{natbib}
 \usepackage{graphicx}
@@
 \subsection{Navarro-Frenk-White (NFW) Profile}
-The NFW profile has had some success in describing dark matter halos is both simulations and observations, though
+The NFW profile has had some success in describing dark matter halos in both simulations and observations, though
 \citep{Navarro1997}
+It is characterized by a scale radius $r_s$ and a dimensionless parameter $\delta_c$, sometimes called the characteristic overdensity \citep{Wright2000}.
 \begin{equation}
@@
 \section{Results}
+%\begin{figure}
+%    \centering
+%    \includegraphics{nfwfitparams.pdf}
+%    \label{}
+%\end{figure}
+
+%\begin{figure}
+%    \centering
+%    \includegraphics{isothermalfitparams.pdf}
+%    \label{}
+%\end{figure}
 
@@
 
-\bibliographystyle{plainnat}
+\bibliographystyle{aasjournal}
 \bibliography{references}

### 2018-05-09 paper.tex
Finished NFW section

@@
 \subsection{Cored Isothermal Sphere Profile}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\textwidth]{isothermalproperties.pdf}
+    \caption{Lensing quantities for a CIS profile with $M_{200} = 10^{15} M_\odot$ and $r_c = 10$ kpc. $z_L = 0.3$ and $z_S = 1.0$.}
+    \label{cisproperties}
+\end{figure}
+
 The cored isothermal sphere (CIS) profile is related to the singular isothermal sphere (SIS) profile, which is often used to describe halos and other collapsed astrophysical objects because of its simple formulation.
@@
 We define $M_{200}$ as the total mass enclosed within $r_{200}$:
-\begin{equation}
+\begin{equation} \label{M200}
 M_{200} = 200 \rho_\mathrm{crit} \frac{4}{3} \pi {r_{200}}^3
@@
 
-Figure \ref{cisproperties} shows the convergence, tangential shear, and ellipticity of a Milky Way-sized halo lens at redshift 0.3 for lensed objects at redshift 1.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\textwidth]{isothermalproperties.pdf}
-    \caption{Lensing quantities for a CIS profile with $M_{200} = 10^{15} M_\odot$ and $r_c = 10$ kpc. $z_L = 0.3$ and $z_S = 1.0$.}
-    \label{cisproperties}
-\end{figure}
+Figure \ref{cisproperties} shows the convergence, tangential shear, and ellipticity of a Milky Way-sized halo lens.
 
 \subsection{Navarro-Frenk-White (NFW) Profile}
-The NFW profile has had some success in describing dark matter halos in both simulations and observations, though
-\citep{Navarro1997}
+The NFW profile has had some success in describing dark matter halos in both simulations and observations \citep{Navarro1997}.
 It is characterized by a scale radius $r_s$ and a dimensionless parameter $\delta_c$, sometimes called the characteristic overdensity \citep{Wright2000}.
+It also depends on the critical density of the universe, which we evaluate at the current time, like before.
+The form of the NFW profile is:
 \begin{equation}
@@
 \end{equation}
-
-%What redshift is $\rho_\mathrm{crit}$ evaluated at? - at halo redshift - can we use current time?
-
-% \begin{equation}\Sigma_\mathrm{NFW}(R) = \frac{2 \rho_\mathrm{crit} \delta_c r_s}{(R/r_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(R/r_s)^2 - 1}}  \arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) \right)
-% \end{equation}
-%
-%
-% \begin{equation}\overline{\Sigma}_\mathrm{NFW}(R) = \frac{4 \rho_\mathrm{crit} \delta_c r_s}{(R/r_s)^2} \left(
-%     \frac{2}{\sqrt{(R/r_s)^2 - 1}} ~\arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) + \ln{\left(\frac{R/r_s}{2}\right)}
-% \right)
-% \end{equation}
-%
-% In terms of angles:
-
-\begin{equation}
+Applying equation \ref{sigma} and defining $\theta_c = r_c/D_L$, we get the projected surface density of the NFW profile:
+\begin{equation} \label{sigmanfw}
 \Sigma_\mathrm{NFW}(\theta) = \frac{2 \rho_\mathrm{crit} \delta_c D_L \theta_s}{(\theta/\theta_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(\theta/\theta_s)^2 - 1}} \arctan\left(\sqrt{\frac{\theta/\theta_s - 1}{\theta/\theta_s + 1}} \right) \right)
 \end{equation}
+\citet{Wright2000} use a slightly different convention for the projected surface density of an NFW profile.
+Note that for $\theta < \theta_s$, the argument of the arctan function in equation \ref{sigmanfw} becomes imaginary.
+However, applying the identity $\arctan(i x) = i\ \mathrm{arctanh}(x)$ and dividing out the $i$ from the square root in the denominator results in the form of $\Sigma_\mathrm{NFW}$ suggested by Wright and Brainerd for when  $\theta < \theta_s$.
+Additionally, their $\theta = \theta_s$ case is just the limit of equation \ref{sigmanfw} when $\theta \rightarrow \theta_s$.
+We argue that all three cases presented are equivalent and therefore we only use one for simplicity.
+\citet{Bartelmann2001} also use our convention.
 
-\begin{equation}
+The average surface density of an NFW profile is:
+\begin{equation} \label{sigmabarnfw}
 \overline{\Sigma}_\mathrm{NFW}(\theta) = \frac{4 \rho_\mathrm{crit} \delta_c D_L \theta_s}{(\theta/\theta_s)^2} \left(
@@
 
-Similar convention used by \citet{Bartelmann2001}
+The equations for tangential shear and ellipticity of an NFW profile are very cumbersome but follow trivially from equations \ref{tangentialshear}, \ref{ellipticity}, \ref{sigmanfw}, and \ref{sigmabarnfw}.
 
-\begin{equation}
-\gamma_\mathrm{NFW}(\theta) = \frac{\overline{\Sigma}_\mathrm{NFW}(\theta) - \Sigma_\mathrm{NFW}(\theta)}{\Sigma_\mathrm{crit}}
+Like the CIS profile, we would like to switch dependence to $M_{200}$ and the concentration parameter $c$ from $r_s$ and $\delta_c$.
+The concentration parameter $c$ is defined as the ratio of $r_{200}$ to the scale radius $r_s$:
+\begin{equation} \label{concentration}
+c = \frac{r_{200}}{r_s}
 \end{equation}
-
-We can calculate ellipticities from tangential shear.
-
-We switch the dependence to $M_{200}$ and $c$ with:
-
+By integrating the NFW density profile spherically out to radius $r_{200}$, we get the form of $M_{200}$:
+\begin{equation} \label{nfwM200}
+M_{200} = M_\mathrm{enc}(r_{200}) = 4 \pi \rho_\mathrm{crit} \delta_c {r_s}^3 \left( \frac{1}{1 + r_{200}/r_s} + \ln{\left(1 + \frac{r_{200}}{r_s} \right)} - 1 \right)
+\end{equation}
+Setting this equal to the definition of $M_{200}$ in equation \ref{M200}, substituting $c$ for $r_{200}$ using equation \ref{concentration}, and solving for $\delta_c$ gives:
 \begin{equation}
@@
 \end{equation}
-\begin{equation}
-r_s = \frac{r_{200}}{c}
-\end{equation}
-\begin{equation}
-r_{200} = \left( \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}} \right)^{1/3}
-\end{equation}
-\begin{equation}
-c = \frac{r_{200}}{r_s}
-\end{equation}
+$r_s$ can be eliminated with equations \ref{concentration} and \ref{M200}.
+Figure \ref{nfwproperties} shows the convergence, tangential shear, and ellipticity of a typical Milky Way-sized NFW halo lens.
 
@@
     \includegraphics[width=0.8\textwidth]{nfwproperties.pdf}
-    \caption{Lensing quantities for a NFW profile with $M_{200} = 10^{15} M_\odot$ and $c = 10$.}
-    \label{}
+    \caption{Lensing quantities for a NFW profile with $M_{200} = 10^{15} M_\odot$ and $c = 10$. Also,  $z_L = 0.3$ and $z_S = 1.0$.}
+    \label{nfwproperties}
 \end{figure}
@@
 \section{Results}
+The parameter fitting results are as shown in figures.
+%figures to be added
+
 %\begin{figure}

### 2018-05-09 paper.tex
Finished data generation section

@@
 % \usepackage{txfonts}
+\usepackage[font=small,labelfont=bf]{caption}
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\textwidth]{isothermalproperties.pdf}
-    \caption{Lensing quantities for a CIS profile with $M_{200} = 10^{15} M_\odot$ and $r_c = 10$ kpc. $z_L = 0.3$ and $z_S = 1.0$.}
-    \label{cisproperties}
-\end{figure}
-
 The cored isothermal sphere (CIS) profile is related to the singular isothermal sphere (SIS) profile, which is often used to describe halos and other collapsed astrophysical objects because of its simple formulation.
@@
 The ellipticity equation, while not quite elegant, is trivial to calculate using equation \ref{ellipticity}.
+Figure \ref{cisproperties} shows the convergence, tangential shear, and ellipticity of a Milky Way-sized halo lens.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\textwidth]{isothermalproperties.pdf}
+    \caption{Lensing quantities for a CIS profile with $M_{200} = 10^{15} M_\odot$ and $r_c = 10$ kpc. $z_L = 0.3$ and $z_S = 1.0$.}
+    \label{cisproperties}
+\end{figure}
 
@@
 
-Figure \ref{cisproperties} shows the convergence, tangential shear, and ellipticity of a Milky Way-sized halo lens.
-
-\subsection{Navarro-Frenk-White (NFW) Profile}
+\subsection{Navarro-Frenk-White (NFW) Profile} \label{nfwsection}
 The NFW profile has had some success in describing dark matter halos in both simulations and observations \citep{Navarro1997}.
@@
 The equations for tangential shear and ellipticity of an NFW profile are very cumbersome but follow trivially from equations \ref{tangentialshear}, \ref{ellipticity}, \ref{sigmanfw}, and \ref{sigmabarnfw}.
+Figure \ref{nfwproperties} shows the convergence, tangential shear, and ellipticity of a typical Milky Way-sized NFW halo lens.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\textwidth]{nfwproperties.pdf}
+    \caption{Lensing quantities for a NFW profile with $M_{200} = 10^{15} M_\odot$ and $c = 10$. Also,  $z_L = 0.3$ and $z_S = 1.0$.}
+    \label{nfwproperties}
+\end{figure}
 
@@
 $r_s$ can be eliminated with equations \ref{concentration} and \ref{M200}.
-Figure \ref{nfwproperties} shows the convergence, tangential shear, and ellipticity of a typical Milky Way-sized NFW halo lens.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\textwidth]{nfwproperties.pdf}
-    \caption{Lensing quantities for a NFW profile with $M_{200} = 10^{15} M_\odot$ and $c = 10$. Also,  $z_L = 0.3$ and $z_S = 1.0$.}
-    \label{nfwproperties}
-\end{figure}
 
 \section{Methods}
+In order to test the distinguishability of CIS and NFW profiles via gravitational lensing shear, we model a lensing scenario with one foreground lens and many background galaxies with random positions and intrinsic ellipticities.
+We calculate the effects of the lens on the shapes of the background galaxies to generate a dataset similar to what one might observe in reality.
+We then attempt to fit both CIS and NFW profiles to the data to see if there is a clear preference for the profile used to generate the data.
+We use the Planck 2015 results for all cosmological parameters \citep{PlanckCollaboration2015}.
 
-\subsection{Modelling of Foreground Lens and Background Galaxies}
-Based on the calculations shown above, we have modelled singular lenses corresponding to each density profile.
- Background galaxies have been generated via randomization of angular coordinates.
+\subsection{Simulated Data Generation}
+We model a single foreground lens halo with an NFW profile using the equations derived in section \ref{nfwsection}.
+The profile has $M_{200} = 10^{15} M_\odot$ and $c = 10$, which are typical values for a Milky Way-sized dark matter halo.
+The lens is placed at redshift $z_L = 0.3$, which is comparable to that of the Bullet Cluster, an interesting lensing target \citep{Clowe2006}.
 
-\begin{enumerate}
-    \item Consider single foreground lens halo with many background galaxies.
-    \begin{itemize}
-        \item Start with one NFW halo, then maybe consider more tests.
-    \end{itemize}
-    \item Construct background galaxies:
-    \begin{itemize}
-        \item Number density on sky: 50 galaxies/square arcminute (LSST, https://arxiv.org/pdf/1305.0793.pdf)
-        \item Intrinsic ellipticity drawn from Gaussian distribution with $\mu=0, \sigma=0.2$ (consistent with https://arxiv.org/pdf/1509.05058.pdf)
-        \item Assume they are all that the same distance $D_S$ since this can be determined by redshift (neglecting some noise)
-        \item Apply shear and deflection angles to background galaxies to get simulated data: $N$ sets of $\epsilon_1$, $\epsilon_2$, $\theta_1$, $\theta_2$
-    \end{itemize}
-    \item Recommended values:
-    \begin{itemize}
-        \item $z_L = 0.3$ (bullet cluster)
-        \item $z_S = 1.0$ (Hubble Deep Field) (also consistent with https://arxiv.org/pdf/1509.05058.pdf)
-        we use the planck 2015 results
-        \item $M_{halo} = 10^{15} M_\odot$
-    \end{itemize}
-\end{enumerate}
+We generate a field of background galaxies within a 1000 arcsecond by 1000 arcsecond square centered on the lens.
+The number of galaxies is chosen so that the average angular number density is 50 galaxies per square arcminute, which is an optimistic expectation for the observing capability of the Large Synoptic Survey Telescope (LSST) \citep{Chang2013}.
+The $(\theta_x, \theta_y)$ coordinates of each background galaxies are generated randomly within the range of the field.
+The intrinsic contributions to the ellipticity components $\epsilon_1$ and $\epsilon_2$ are also randomly sampled from a Gaussian distribution with mean $\mu_\epsilon = 0$ and standard deviation $\sigma_\epsilon = 0.2$.
+This is consistent with the findings of \citet{Niemi2015} from observations.
+We place all galaxies at the same redshift $z_S = 1.0$, which is comparable to many objects in the Hubble Deep Field.
+This is justified because redshift can be simple to determine and account for when analyzing lensing in observational data.
 
-Estimating ellipticity has well-documented issues [cite] due to noise and PSF
+We apply lensing shear to all the background galaxies based on their distance from the center of the halo, assuming that ellipticities add together linearly.
+We neglect the application of deflection angles since this would have little effect on fitting, and shear is derived as a function of image position rather than source position.
+Effectively, we assume all galaxies are already at their deflected position.
+Also, the majority of the background galaxies lie in the weak lensing regime, where the deflection angle can be negligible.
+The result is a simulated dataset with $N$ galaxies, and $N$ corresponding sets of  $\{\theta_x, \theta_y, \epsilon_1, \epsilon_2\}$.
+
+Figure \ref{ellipticityexample} illustrates the effects of shear by both CIS and NFW profiles on a background galaxy field.
+The galaxy number density is exaggerated in comparison to the one used to generate data for actual analysis.
+The strong lensing regime is apparent near the center, where tangential ellipticity is negative and there is an impression of critical curves (compare to figures \ref{cisproperties} and \ref{nfwproperties}).
+The two profiles are nearly impossible to distinguish by eye, but precise data and statistics will offer a different picture.
 
@@
     \includegraphics[width=0.49\textwidth]{nfwellipticities.pdf}
-    \caption{plots}
-    \label{}
+    \caption{Simulated lensing of a field of background galaxies by a CIS lens (left) and NFW lens (right).
+Each line represents a single galaxy.
+Intrinsic ellipticities are drawn from a Gaussian distribution of mean 0 and standard deviation 0.2.
+The length of the line indicates the post-lensing ellipticity, while the orientation represents the direction that the galaxy is sheared.}
+    \label{ellipticityexample}
 \end{figure}
 
-\subsection{Data Analysis and Density Profile Determination}
-\begin{enumerate}
-\item Bin galaxies in annuli by $\theta$ value (use log bins for theta)
-\item Calculate mean and standard deviation of ellipticity
-\item Attempt to fit both NFW and isothermal profiles, see if the fit is distinguishable
-\end{enumerate}
+\subsection{Data Analysis and Fitting}
+To reconstruct a shear profile of the lens, we bin the galaxies into 40 linearly spaced annuli by their $\theta$ magnitude. The bins extend from from 10" out to approximately 700". Within each bin, we
+and form a
+
+Calculate mean and standard deviation of ellipticity
+Attempt to fit both NFW and isothermal profiles, see if the fit is distinguishable
+
+we fit expressions for ellipticity
+
+We fit by numerically minimizing $\chi^2$
+\begin{equation}
+\chi^2 =
+\end{equation}
 
@@
 The parameter fitting results are as shown in figures.
-%figures to be added
-
-%\begin{figure}
-%    \centering
-%    \includegraphics{nfwfitparams.pdf}
-%    \label{}
-%\end{figure}
-
-%\begin{figure}
-%    \centering
-%    \includegraphics{isothermalfitparams.pdf}
-%    \label{}
-%\end{figure}
 
@@
 
+may want to try fitting to CIS-generated data
+
+Estimating ellipticity has well-documented issues [cite] due to noise and PSF
+
 ignore cosmic shear (https://journals.aps.org/prd/pdf/10.1103/PhysRevD.70.023008)

### 2018-05-09 paper.tex
Finished introduction

@@
 Two commonly used density profiles in the field are the isothermal profile and the Navarro-Frenk-White (NFW) profile.
-The NFW profile has been found to fit simulated dark matter halos very well \citep{}, while the isothermal profile results from an idealized isothermal collapse \citep{}.
-Both profiles extend to infinity
+The NFW profile has been found to fit simulated dark matter halos very well \citep{Navarro1997}, while the isothermal profile results from an idealized isothermal collapse \citep{Shapiro1999}.
+It is of great interest to determine the general forms of halo density profiles since this tells us about structure formation and the nature of dark matter \citep{Frenk2012}.
+Lensing offers one of the few ways to probe the distribution of all matter, not just baryonic matter.
+Other methods include using optical rotation curves, which present difficulties \citep{Jimenez2003}.
 
-It is of great interest to determine the general forms of halo density profiles
-since this tells us about structure formation and the nature of dark matter
-\citep{}
-Lensing offers one of the few ways to probe the distribution of all matter, not just baryonic matter.
-rotation curve present difficulties (https://arxiv.org/pdf/astro-ph/0201352.pdf)
-
-In this paper, we will investigate the distinguishability of NFW and isothermal profiles
-given galaxy-galaxy lensing data
-The goal of this project is to devise a method to analyze lensed galaxy cluster data and find which density profile is more probable between the isothermal and NFW profiles.
-In order to do so, we generate simulated data sets and analyze them to find the more probable profiles they would fit into.
-This analysis method is expected to be usable in determining the characteristics of real observed data as well.
-
-Outline:
-We start by introducing the general lensing characteristics of spherical density profiles, followed by the specifics for cored isothermal and NFW profiles. We then describe
-The results
+In this paper, we will investigate the distinguishability of NFW and isothermal profiles using galaxy-galaxy lensing data.
+We derive the lensing characteristics of cored isothermal and NFW profiles and apply them towards generating a simulated data set of background galaxy lensing.
+We then attempt to fit both profiles to determine if one is significantly more likely than the other.
+These methods are expected to be applicable towards determining the characteristics of real observed data as well.
 
@@
 Intrinsic ellipticities are drawn from a Gaussian distribution of mean 0 and standard deviation 0.2.
-The length of the line indicates the post-lensing ellipticity, while the orientation represents the direction that the galaxy is sheared.}
+The length of the line indicates the post-lensing ellipticity, while the orientation represents the final orientation of the galaxy's ellipticity.}
     \label{ellipticityexample}
@@
 \subsection{Data Analysis and Fitting}
-To reconstruct a shear profile of the lens, we bin the galaxies into 40 linearly spaced annuli by their $\theta$ magnitude. The bins extend from from 10" out to approximately 700". Within each bin, we
-and form a
-
-Calculate mean and standard deviation of ellipticity
-Attempt to fit both NFW and isothermal profiles, see if the fit is distinguishable
+To reconstruct a shear profile of the lens, we bin the galaxies into 40 linearly spaced annuli by their $\theta$ magnitude.
+The bins extend from from 10" out to approximately 700".
+Within each bin, we calculate the mean and standard deviation of ellipticity of the population of galaxies that it contains.
+We attempt to fit this data to the theoretical ellipticities of  both CIS and NFW and isothermal profiles, see if the fit is distinguishable
 
@@
 
-%What theta range should we look at? (5 arcminutes?)
-
 %How to properly do sigma contours?
@@
 \section{Results}
+The results of fitting
 The parameter fitting results are as shown in figures.
+
+We apply Bayesian evidence to
 
@@
 But also, weak lensing can in fact provide sufficient distinguishability
+
+though the evidence ratio is much smaller when only fitting with larger radii
 

### 2018-05-09 paper.tex
Finished methods and results

@@
 where $\sigma^2$ is the velocity dispersion of the halo \citep{Chen2005, Shapiro1999}.
-Applying equation \ref{sigma} and defining $\theta_c = r_c/D_L$, we get the projected surface density of the CIS profile:
+Applying Equation \ref{sigma} and defining $\theta_c = r_c/D_L$, we get the projected surface density of the CIS profile:
 \begin{equation}
@@
 \end{equation}
-The average surface density inside angular radius $\theta$ is derived using equation \ref{sigmabar}:
+The average surface density inside angular radius $\theta$ is derived using Equation \ref{sigmabar}:
 \begin{equation}
@@
 \end{equation}
-The tangential shear follows from equation \ref{tangentialshear}:
+The tangential shear follows from Equation \ref{tangentialshear}:
 \begin{equation}
@@
 \end{equation}
-The ellipticity equation, while not quite elegant, is trivial to calculate using equation \ref{ellipticity}.
+The ellipticity equation, while not quite elegant, is trivial to calculate using Equation \ref{ellipticity}.
 Figure \ref{cisproperties} shows the convergence, tangential shear, and ellipticity of a Milky Way-sized halo lens.
@@
 \end{equation}
-We also calculate $M_{200}$ specifically for a CIS profile by integrating equation \ref{cisdensity}:
+We also calculate $M_{200}$ specifically for a CIS profile by integrating Equation \ref{cisdensity}:
 \begin{equation} \label{cisM200}
@@
 \end{equation}
-We can now completely switch the CIS profile's dependence from $\sigma^2$ to $M_{200}$ with equation \ref{r200} and solving for $\sigma^2$ from equation \ref{cisM200}:
+We can now completely switch the CIS profile's dependence from $\sigma^2$ to $M_{200}$ with Equation \ref{r200} and solving for $\sigma^2$ from Equation \ref{cisM200}:
 \begin{equation}
@@
 \end{equation}
-Applying equation \ref{sigma} and defining $\theta_c = r_c/D_L$, we get the projected surface density of the NFW profile:
+Applying Equation \ref{sigma} and defining $\theta_c = r_c/D_L$, we get the projected surface density of the NFW profile:
 \begin{equation} \label{sigmanfw}
@@
 \citet{Wright2000} use a slightly different convention for the projected surface density of an NFW profile.
-Note that for $\theta < \theta_s$, the argument of the arctan function in equation \ref{sigmanfw} becomes imaginary.
+Note that for $\theta < \theta_s$, the argument of the arctan function in Equation \ref{sigmanfw} becomes imaginary.
 However, applying the identity $\arctan(i x) = i\ \mathrm{arctanh}(x)$ and dividing out the $i$ from the square root in the denominator results in the form of $\Sigma_\mathrm{NFW}$ suggested by Wright and Brainerd for when  $\theta < \theta_s$.
-Additionally, their $\theta = \theta_s$ case is just the limit of equation \ref{sigmanfw} when $\theta \rightarrow \theta_s$.
+Additionally, their $\theta = \theta_s$ case is just the limit of Equation \ref{sigmanfw} when $\theta \rightarrow \theta_s$.
 We argue that all three cases presented are equivalent and therefore we only use one for simplicity.
@@
 \end{equation}
-Setting this equal to the definition of $M_{200}$ in equation \ref{M200}, substituting $c$ for $r_{200}$ using equation \ref{concentration}, and solving for $\delta_c$ gives:
+Setting this equal to the definition of $M_{200}$ in Equation \ref{M200}, substituting $c$ for $r_{200}$ using Equation \ref{concentration}, and solving for $\delta_c$ gives:
 \begin{equation}
@@
 Within each bin, we calculate the mean and standard deviation of ellipticity of the population of galaxies that it contains.
-We attempt to fit this data to the theoretical ellipticities of  both CIS and NFW and isothermal profiles, see if the fit is distinguishable
-
-we fit expressions for ellipticity
-
-We fit by numerically minimizing $\chi^2$
+We attempt to fit this data to the theoretical ellipticities of both CIS and NFW profiles, considering the uncertainty on the mean ellipticity in each bin to be $\sigma / \sqrt{N}$, where $\sigma$ is the standard deviation of ellipticity in the bin (close to 0.2) and $N$ is the number of galaxies in the bin.
+We fit by numerically minimizing a $\chi^2$ expression:
 \begin{equation}
-\chi^2 =
+\chi^2 = \sum_i{\left(\frac{\epsilon_\mathrm{model}(\theta_i) - \epsilon_i}{\sigma_i}\right)^2},
 \end{equation}
-
-%How to properly do sigma contours?
+where $\theta_i$ is the midpoint of bin $i$, $\epsilon_i$ is the mean ellipticity of the bin, and $\sigma_i$ is the uncertainty on the mean ellipticity of the bin.
 
 \section{Results}
-The results of fitting
-The parameter fitting results are as shown in figures.
+The results of fitting are shown in Figure \ref{fits}.
+When fitting the simulated data with an NFW profile, we  get best fit values of $M_{200} = 1.021 \times 10^{15} M_\odot$ and $c = 10.13$.
+When fitting to a CIS profile, the best fit parameters are $M_{200} = 1.568 \times 10^{15} M_\odot$ and $\theta_c = 0.429^{\prime \prime}$.
+The NFW fit is quite accurate, and the actual original parameters of the lens halo lie within the $1\sigma$ contour shown in Figure \ref{fits}.
+The CIS fit overestimates the mass and gives a core radius of about 2 kpc.
 
-We apply Bayesian evidence to
+We apply Bayesian evidence to quantify the likelihood of one model being the correct fit over another. We express the Bayesian evidence ratio $K$ as:
+\begin{equation}
+K = \frac{\int dM_{200} dc\ e^{\chi^2_\mathrm{NFW} / 2} P(M_{200}) P(c)}{\int dM_{200} d\theta_c\ e^{\chi^2_\mathrm{CIS} / 2} P(M_{200}) P(\theta_c)}
+\end{equation}
+The integrals are over the parameter ranges indicated in Figure \ref{fits} and $P(M_{200})$, $P(c)$, and $P(\theta_c)$ are flat priors over the same parameter ranges.
+We obtain an evidence ratio $K = 1.62 \times 10^7$, which very strongly indicates that the NFW model is correct (and it is).
+While this may seem excessively large, it is easily justified by the best fit $\chi^2$ values, which are 47.8 for NFW and 83.1 for CIS.
+$e^{\Delta \chi^2 / 2} \sim 10^7$, which is the right order of magnitude.
+Figure \ref{fitcomparison} shows how the slight differences in ellipticity profiles results in a worse fit for the CIS profile.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.49\textwidth]{isothermalfitparams.png}
+    \includegraphics[width=0.5\textwidth]{nfwfitparams.png}
+    \caption{Normalized probability densities for fit parameters for CIS profile (left) and NFW profile (right).
+The best fit values are shown as a red dot, while for the NFW fit, the original halo's properties are indicated by a green dot.
+68\%, 95\%, and 99.7\% confidence contours are delineated by white dashed lines.}
+    \label{fits}
+\end{figure}
 
@@
     \includegraphics[width=0.9\textwidth]{comparison.pdf}
-    \caption{plots}
-    \label{}
+    \caption{Comparison of the lensing-induced ellipticity over the angular range of the simulated dataset for the original lens, CIS fit, NFW fit, and binned data including uncertainties.}
+    \label{fitcomparison}
 \end{figure}
-
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=0.49\textwidth]{isothermalfitparams.pdf}
-%     \includegraphics[width=0.49\textwidth]{nfwfitparams.pdf}
-%     \caption{plots}
-%     \label{}
-% \end{figure}
 
@@
 
-Like (COMPARISONS BETWEEN ISOTHERMAL AND NFW MASS PROFILES
-FOR STRONG-LENSING GALAXY CLUSTERS), we find that the strong lensing regime provides the most
-But also, weak lensing can in fact provide sufficient distinguishability
+Like \citet{Shu2008}, we find that the strong lensing regime provides a strong
+
+But also, weak lensing can in fact provide very sufficient distinguishability
+By combining weak and near-strong lensing
 

### 2018-05-09 paper.tex
Finished paper

@@
 \usepackage{amsmath}
-% \usepackage{txfonts}
 \usepackage[font=small,labelfont=bf]{caption}
@@
 We examine the feasibility of distinguishing NFW and cored isothermal density profiles using weak gravitational lensing shear.
-
-We model lenses in the two different profiles, as well as background galaxies to be lensed.
-Analyzing the simulated data of these lensed galaxies gives us insight into how we can distinguish the differences between the two profiles.
-This method is expected to be helpful in the analysis of real observation data in the future.
+We simulate a lensing scenario with one foreground lens acting on a field of background galaxies with random positions and intrinsic ellipticities, calculating the shearing of galaxy shapes.
+We then attempt to fit both isothermal and NFW profiles to the data to see if there is a clear preference for the profile used to generate the data.
+We find that dataset allows for excellent distinguishability between the profiles, with a Bayesian evidence ratio of $1.62 \times 10^7$.
+This method is expected to be useful in the analysis of observed data in the future.
 \end{abstract}
@@
 Lensing offers one of the few ways to probe the distribution of all matter, not just baryonic matter.
-Other methods include using optical rotation curves, which present difficulties \citep{Jimenez2003}.
+Other methods include using optical rotation curves, which have presented difficulties \citep{Jimenez2003}.
 
 In this paper, we will investigate the distinguishability of NFW and isothermal profiles using galaxy-galaxy lensing data.
-We derive the lensing characteristics of cored isothermal and NFW profiles and apply them towards generating a simulated data set of background galaxy lensing.
-We then attempt to fit both profiles to determine if one is significantly more likely than the other.
+First, we derive the lensing characteristics of cored isothermal and NFW profiles and apply them towards generating a simulated data set of background galaxy lensing.
+We then attempt to fit both profiles to the data to determine if one is significantly more likely than the other.
 These methods are expected to be applicable towards determining the characteristics of real observed data as well.
@@
 \end{equation}
-$r_s$ can be eliminated with equations \ref{concentration} and \ref{M200}.
+$r_s$ can be eliminated with equations \ref{concentration} and \ref{r200}.
 
@@
 Intrinsic ellipticities are drawn from a Gaussian distribution of mean 0 and standard deviation 0.2.
-The length of the line indicates the post-lensing ellipticity, while the orientation represents the final orientation of the galaxy's ellipticity.}
+The length of the line indicates the post-lensing ellipticity, while the orientation represents the final orientation of the image's ellipticity.}
     \label{ellipticityexample}
@@
 \begin{equation}
-K = \frac{\int dM_{200} dc\ e^{\chi^2_\mathrm{NFW} / 2} P(M_{200}) P(c)}{\int dM_{200} d\theta_c\ e^{\chi^2_\mathrm{CIS} / 2} P(M_{200}) P(\theta_c)}
+K = \frac{\int dM_{200} dc\ e^{-\chi^2_\mathrm{NFW} / 2} P(M_{200}) P(c)}{\int dM_{200} d\theta_c\ e^{-\chi^2_\mathrm{CIS} / 2} P(M_{200}) P(\theta_c)}
 \end{equation}
@@
 
+\newpage
+
 \section{Conclusions}
+We find that the simulated measurements we made provide excellent distinguishability between cored isothermal profiles and NFW profiles.
+Using weak lensing alone can in fact provide very sufficient distinguishability, though the evidence ratio is much smaller when only fitting with larger radii ($> 100^{\prime \prime}$ in this case).
+By combining weak and near-strong lensing (down to $10^{\prime \prime}$), we are able to dramatically increase the evidence ratio.
+Uncertainties on mass measurements are around the 10\% level.
 
-Like \citet{Shu2008}, we find that the strong lensing regime provides a strong
+The idea of constraining lens profile parameters has been applied to many observations before \citep{Bartelmann1996}, but not in the context of comparing density profiles using strong and weak lensing.
+However, this concept is highly dependent on good data.
+As an example, \citet{Shu2008} looked at comparing NFW and isothermal profile fits in strong lensing with a focus on arcs, and found differing levels of distinguishibility for different lenses.
+Observational studies also face the issue of cosmic shear \citep{Dodelson2004}.
 
-But also, weak lensing can in fact provide very sufficient distinguishability
-By combining weak and near-strong lensing
+Our method was successful in the few controlled cases we tested, able to strongly distinguish the different lens density profiles.
+For fairness, we may want to try fitting both profiles to CIS-generated data.
+When analyzing real observed data, we expect the evidence ratio to further decrease due to noise and uncertainties.
+We still expect that plenty can be learned from applying this method to observational data from advanced telescopes in the near future.
 
-though the evidence ratio is much smaller when only fitting with larger radii
-
-has been applied to observations before
-https://arxiv.org/pdf/astro-ph/9602053.pdf
-but not in the context of comparing density profiles using for strong and weak
-but this is highly dependent on good data
-
-http://iopscience.iop.org/article/10.1086/590049/pdf looked at NFW vs isothermal in strong lensing with a focus on arcs, and found differing levels of distinguishibility for different lenses.
-
-https://arxiv.org/pdf/1101.0650.pdf - our results don't match
-
-may want to try fitting to CIS-generated data
-
-Estimating ellipticity has well-documented issues [cite] due to noise and PSF
-
-ignore cosmic shear (https://journals.aps.org/prd/pdf/10.1103/PhysRevD.70.023008)
-
-From our data analysis, we were able to find the more probable density profile of a simulated data set.
-Since the simulated data is based on the NFW and isothermal profile models, we were able to decisively distinguish between the two.
-When analyzing real observed data, we expect the probability ratios to be relatively more even.
-Future goals include the use of these methods to analyze observed data of galaxy clusters to find the density profile of their lenses.
-
-%Where to go from here?
-
+{
+\linespread{1.0}
+\selectfont
 \bibliographystyle{aasjournal}
 \bibliography{references}
+}
 
